\section{The Proof-Layer Bridge and Its Witness-Layer Boundary}
\label{sec:theorem}

\subsection{The positive flagship}
\label{sec:positive}

\begin{theorem}[Generic obstruction bridge]
\label{thm:bridge}
For any voter type \(\mathtt{Voter}\), any finite decidable alternative type \(\mathtt{Alt}\), and every
\(F : \mathtt{SWF}\ \mathtt{Voter}\ \mathtt{Alt}\),
if \(\mathtt{UN}\ F\) and \(\mathtt{MINLIB}\ F\) hold, then \(\mathtt{SenOutcomeObstruction}\ F\).
\end{theorem}

\begin{theorem}[Generic impossibility from the obstruction basis]
\label{thm:generic-impossibility}
Under the same assumptions, \(\neg\,\mathtt{SocialAcyclic}\ F\).
\end{theorem}

\begin{corollary}[Legacy finite lift]
\label{thm:lift}
For all natural numbers \(n,m\) with \(2 \leq n\) and \(4 \leq m\), for every social welfare function
\(F : \mathtt{SWF}\ (\mathtt{Fin}\ n)\ (\mathtt{Fin}\ m)\),
if \(\mathtt{UN}\ F\) and \(\mathtt{MINLIB}\ F\) hold, then \(\neg\, \mathtt{SocialAcyclic}\ F\).
\end{corollary}

\begin{remark}[Statement form in Lean]
\label{rem:lean-form}
Theorem~\ref{thm:bridge} is the Lean theorem
\texttt{sen\_outcome\_}\allowbreak\texttt{obstruction\_of\_UN\_MINLIB} at
\code{SocialChoiceAtlas/Sen/ObstructionBridge.lean}.
Theorem~\ref{thm:generic-impossibility} is
\texttt{sen\_impossibility\_}\allowbreak\texttt{from\_obstruction\_basis} in the same module.
Corollary~\ref{thm:lift} is the existing theorem
\texttt{sen\_impossibility\_lifts} at
\code{SocialChoiceAtlas/Sen/Lifting/ImpossibilityLift.lean}.
The corollary keeps the public theorem name and statement shape for downstream compatibility, but its proof body is now the specialization of the generic theorem.
\end{remark}

\begin{remark}[The legacy \(\mathtt{\_hn}\) and \(\mathtt{\_hm}\) hypotheses]
\label{rem:hm-unused}
The generic obstruction theorem has no explicit voter- or alternative-cardinality lower-bound hypotheses.
The legacy theorem retains \(\mathtt{\_hn : 2 \leq n}\) and \(\mathtt{\_hm : 4 \leq m}\) solely for backward-compatible alignment with the former statement.
This is not a claim that \(\mathtt{UN \wedge MINLIB}\) implies \(\mathtt{4 \leq m}\).
\(\mathtt{MINLIB}\) supplies two distinct rights holders and two decisive alternative pairs, while the O2/O3/O4 classification determines whether the distinguished alternative support has cardinality \(2\), \(3\), or \(4\).
\end{remark}

\paragraph{Theorem ladder.}
The bridge is factored through public objects rather than hidden case analysis:

\begingroup
\renewcommand{\arraystretch}{1.15}
\noindent\begin{tabularx}{\linewidth}{@{}l X X@{}}
\toprule
Step & Mathematical role & Lean binding \\
\midrule
T1 & Witness extraction from \(\mathtt{MINLIB}\) & \texttt{exists\_senRightsWitness}, \texttt{exists\_classified\_}\allowbreak\texttt{senRightsWitness} in \code{ObstructionBasis.lean} \\
T2 & Exhaustive O2/O3/O4 overlap classification & \texttt{classify\_raw\_overlap}, \texttt{ClassifiedSenRightsWitness.kind} in \code{ObstructionBasis.lean} \\
T3 & Exact support cardinality & \texttt{ClassifiedSenRightsWitness.}\allowbreak\texttt{support\_card\_eq\_kind} in \code{ObstructionSoundness.lean} \\
T4 & Shape soundness & \texttt{outcome\_of\_twoOverlap}, \texttt{outcome\_of\_zOnly}, \texttt{outcome\_of\_wOnly}, \texttt{outcome\_of\_disjoint} in \code{ObstructionSoundness.lean} \\
T5 & Outcome refutation & \texttt{SenOutcomeObstruction.}\allowbreak\texttt{refutes\_socialAcyclic} in \code{ObstructionSoundness.lean} \\
T6 & Obstruction bridge & \texttt{sen\_outcome\_obstruction\_}\allowbreak\texttt{of\_UN\_MINLIB} in \code{ObstructionBridge.lean} \\
T7 & Generic impossibility & \texttt{sen\_impossibility\_}\allowbreak\texttt{from\_obstruction\_basis} in \code{ObstructionBridge.lean} \\
T8 & Legacy lift corollary & \texttt{sen\_impossibility\_lifts} in \code{ImpossibilityLift.lean} \\
\bottomrule
\end{tabularx}
\endgroup

\paragraph{Shape reading.}
O2 means the two decisive pairs use the same two alternatives, up to orientation; it yields a strict conflict on that pair.
O3 means exactly one endpoint overlaps; it yields a 3-cycle.
O4 means the two decisive pair supports are disjoint; it yields a 4-cycle.
These are semantic profile constructions over the ambient voter type, not literal restricted SWFs.

\begin{remark}[What this is, what this is not]
\label{rem:lift-scope}
Theorems~\ref{thm:bridge} and~\ref{thm:generic-impossibility} are Lean Proof-layer statements.
They say that Sen's semantic contradiction factors through a complete finite family of bounded obstruction shapes.
They do \emph{not} say that the Sen24 CNF encoding extends to such cases; they do \emph{not} say that any short-cycle CNF approximation lifts; and they do \emph{not} say that any repair presentation extends canonically.
These are separate questions, addressed in Section~\ref{sec:negative} and deferred to a companion paper respectively.
\end{remark}

\subsection{The scope wall between Proof layer and Witness/Audit layer}
\label{sec:negative}

The positive bridge establishes proof-level transfer to full acyclicity.
It does not establish witness-level transfer.
The CNF Witness/Audit layer in this repository uses the short-cycle encoding \(\mathtt{no\_cycle3} \wedge \mathtt{no\_cycle4}\) as a stand-in for full acyclicity.
At the Sen24 base case \((n,m)=(2,4)\), the equivalence between \(\mathtt{no\_cycle3} \wedge \mathtt{no\_cycle4}\) and full acyclicity on the social strict relation was audited exhaustively by \code{scripts/check\_acyclicity\_short\_cycles.py}.
At larger cases that audited equivalence does not transfer automatically: \(\mathtt{no\_cycle3} \wedge \mathtt{no\_cycle4}\) still permits length-5 cycles at \(m = 5\), as documented in \code{docs/no\_cycle\_interpretation\_note.md}.
Accordingly, evidence using these levers should be interpreted only within the local-rationality family they induce, not as evidence about full acyclicity at the family scale.

\begin{proposition}[Scope wall]
\label{prop:scope-wall}
The Lean Proof-layer bridge does not automatically upgrade the Sen24 CNF atlas into a family-level CNF certificate for full \code{SocialAcyclic}.
The CNF Witness/Audit layer at \(m \geq 5\) remains scoped to the audited short-cycle encoding \(\mathtt{no\_cycle3} \wedge \mathtt{no\_cycle4}\), whose equivalence to full acyclicity was audited only at \(m = 4\).
A family-level CNF certificate for full acyclicity requires a stronger rationality encoding to be introduced and audited separately at the Witness/Audit layer.
\end{proposition}

\paragraph{Witness for the $m=5$ gap (prose).}
The boundary in Proposition~\ref{prop:scope-wall} is exhibited concretely by an asymmetric directed $5$-cycle.
Take five distinct alternatives $a_0,a_1,a_2,a_3,a_4 \in \mathtt{Fin\ 5}$ and let the social strict preference relation contain exactly the five oriented edges
\(a_0 \succ a_1,\; a_1 \succ a_2,\; a_2 \succ a_3,\; a_3 \succ a_4,\; a_4 \succ a_0\),
with no other strict edges (in particular, no chord and no reverse edge).
This relation is asymmetric by construction, and direct inspection of every $3$-subset and every $4$-subset of $\{a_0,\dots,a_4\}$ shows that no length-3 cycle and no length-4 cycle is present, so it satisfies the short-cycle conjunction \(\mathtt{no\_cycle3} \wedge \mathtt{no\_cycle4}\).
The relation is nonetheless not acyclic, since the length-5 oriented cycle on $a_0,a_1,a_2,a_3,a_4$ violates \(\mathtt{SocialAcyclic}\).
Hence at \(m = 5\) the short-cycle conjunction does not entail full acyclicity, and a CNF artifact whose only rationality clauses are \(\mathtt{no\_cycle3} \wedge \mathtt{no\_cycle4}\) cannot, by itself, certify full acyclicity at the family scale.
This is a prose witness recorded in the manuscript; we do not formalise it as a Lean theorem here, in line with the audit-policy status of Proposition~\ref{prop:scope-wall}.

\paragraph{Status.}
Proposition~\ref{prop:scope-wall} is a guarantee-boundary statement and an audit-policy statement, not a Lean theorem.
It is recorded in \code{docs/m2\_scope\_wall.md} and bound to the existing finite audit in \code{scripts/check\_acyclicity\_short\_cycles.py}.
Promoting it to a Lean theorem would require formalising the short-cycle encoding as a Lean-side relation and proving the non-equivalence at \(m = 5\); we leave that to future work, in line with the precedent from the Explanation-Contract paper that finite-witness legitimisation is text-first when the formalisation cost is asymmetric to the content.

\paragraph{Reading the boundary.}
The boundary recorded here is between layers, not between theorem families.
It is incorrect to read this paper as saying ``Sen's theorem holds in the local-rationality family but not in full acyclicity'': the kernel-checked positive bridge already concludes at full \(\mathtt{SocialAcyclic}\) at the Proof layer.
The point of the scope wall is that the \emph{CNF artifact} that backed the Sen24 evidence does not by itself become a CNF artifact for the larger case; a separately audited encoding contract is required at the Witness/Audit layer.
