\section{Related Work \& Positioning}
\label{sec:related}

\paragraph{SAT-based finite witnesses in social choice.}
The line of work using SAT and automated reasoning to certify finite social-choice impossibility instances goes back at least to \citet{tanglin2009computer} and is developed further by \citet{geist2011automated} and \citet{brandtgeist2016strategyproof}.
This paper belongs to the same lineage on the artifact side: the base-case CNF witness used by the Evidence-Contract paper sits inside that tradition.
Our contribution is orthogonal: it is not a new SAT-based existence result, but a kernel-checked Lean Proof-layer lift that does \emph{not} use a SAT certificate to extend the base case.
It also makes an explicit witness-layer scope wall against the assumption that a base-case CNF certificate is a family-level CNF certificate.
The framing we adopt is comparative rather than corrective: \citet{tanglin2009computer} and \citet{geist2011automated} already establish, in different settings, that base-case SAT-based finite-witness evidence carries real scope conditions and per-instance interpretive caveats, and \citet{brandtgeist2016strategyproof} similarly fixes a base case before drawing conclusions.
What is new here, to our reading, is not the observation that such scope conditions exist, but their packaging as an explicit Proof-vs-Witness/Audit transfer contract: a layer-level statement, recorded alongside the artifact, that the Proof-layer lift is kernel-checked while the CNF Witness/Audit layer remains scoped to a separately audited encoding contract.

\paragraph{Formal verification and certified SAT checking.}
The trust model used by the Evidence-Contract paper for the base case, and inherited here for the Proof layer, rests on Lean~4 \citep{moura2021lean4} for kernel-checked semantic proofs and on certified RAT/DRAT checking \citep{cruzfilipe2017lrat,wetzler2014drat} for the CNF witness side.
Mechanized formalizations of social-choice theorems in proof assistants are themselves an established line \citep{nipkow2009social}.
The present paper does not propose a new prover, a new clausal-proof format, or a new general mechanized social-choice theorem.
Its contribution relative to that background is a kernel-checked Lean polymorphic lift of the Sen base case to the family, deliberately scoped so that the certified-checking infrastructure remains a witness-layer concern and is not re-claimed at the family scale.

\paragraph{Lifting in computational social choice.}
The lifting question---whether an axiomatic structure verified on small instances extends to larger instances---has a developed literature in judgment aggregation and binary aggregation, including \citet{grandiendriss2013}.
Our positive flagship is a particular polymorphic instance of this question for Sen's liberal paradox, delivered at the kernel-checked Lean level rather than via a separate transfer theorem.
The methodological point inherited from this literature, and made sharper here, is that the lift question is per-axiom and per-property; our contribution is to show that for Sen's liberal paradox a polymorphic semantic proof suffices, and to make the corresponding witness-layer non-lift explicit as a scope wall.

\paragraph{Assumption-based diagnosis and MUS/MCS.}
The non-canonicity of repair presentation studied in the Explanation-Contract paper is close in spirit to assumption-based and diagnosis-oriented work, including \citet{dekleer1986atms}.
At family scale, this question becomes whether the \emph{representation} under which repairs are reported transfers when the case is enlarged.
This paper does not address this question at family scale; we leave it to a companion paper in preparation (Section~\ref{sec:conclusion}).
The reason for the deferral is methodological, not technical: a family-scale representation-non-canonicity result requires fixing the witness class (bundled vs.\ split vs.\ clause-equivalent re-encoding) and its generator interface before exploration scripts proliferate.

\paragraph{Position relative to the Evidence- and Explanation-Contract papers.}
The Evidence-Contract paper established that the Sen24 base case is diagnosable as Proof / Audit / Witness.
The Explanation-Contract paper established that raw repair presentation is not canonical under clause-multiset equivalence at the base case.
This paper, the Transfer Contract, establishes that the Proof layer lifts unconditionally to all finite cases satisfying the same semantic axioms, while the Witness/Audit layer does not lift automatically.
The four-contract program intentionally keeps these contracts separated: the Evidence Contract is about diagnosability of the base case, the Explanation Contract is about presentation-canonicity at the base case, and the Transfer Contract is about layer-level transfer to the family.
The present paper thereby closes the chain that begins with the kernel-checked base case of the Evidence Contract: every claim that the Sen24 evidence transfers must now route through a separate Witness/Audit audit, even though the Proof-layer transfer is itself kernel-checked.

\paragraph{What this paper is \emph{not}.}
The paper does not propose a new SAT or MUS/MCS algorithm.
It does not claim a speed result or a hardness flagship.
It does not claim that the polymorphic Lean lift here is novel as social-choice mathematics: the underlying argument is Sen's, and the case-split structure is the one already used at the base case in this repository.
The novelty is in the auditable-abstraction layer: a kernel-checked Lean lift that reaches full \(\mathtt{SocialAcyclic}\), paired with an explicit scope wall to the CNF Witness/Audit layer.
