\section{Reproducibility Note}
\label{sec:repro}

This manuscript is grounded in kernel-checked Lean modules and repository-local reproducibility artifacts rather than new solver experiments.
The main evidence sources used in the text are:

\begin{itemize}[leftmargin=1.5em]
\item \code{SocialChoiceAtlas/Sen/ObstructionBasis.lean} --- witness extraction and O2/O3/O4 classification.
\item \code{SocialChoiceAtlas/Sen/ObstructionProfiles.lean} --- generic prefix rankings and ambient two-ranking profiles.
\item \code{SocialChoiceAtlas/Sen/ObstructionSoundness.lean} --- exact support cardinalities, shape soundness, and outcome refutation.
\item {\sloppy\code{SocialChoiceAtlas/Sen/ObstructionBridge.lean} --- the generic bridge theorems \texttt{sen\_outcome\_obstruction\_of\_UN\_MINLIB} and \texttt{sen\_impossibility\_from\_obstruction\_basis}.\par}
\item \code{SocialChoiceAtlas/Sen/Lifting/ImpossibilityLift.lean} --- the legacy compatibility corollary \(\mathtt{sen\_impossibility\_lifts}\).
\item \code{SocialChoiceAtlas.lean} --- the root import lines that wire the bridge and compatibility theorem into the default \(\mathtt{lake\ build}\).
\item \code{scripts/ci\_m2\_smoke.sh} --- the M2 smoke gate for bridge imports, theorem anchors, and placeholder scans.
\item \code{docs/m2\_scope\_wall.md} --- the scope wall.
\item \code{docs/no\_cycle\_interpretation\_note.md} and \code{docs/axiom\_semantics\_scaling.md} --- the prior repository notes that establish why the short-cycle encoding does not transfer past \(m = 4\).
\item \code{scripts/check\_acyclicity\_short\_cycles.py} --- the finite check that audits the short-cycle encoding at the base case.
\end{itemize}

\subsection{Zenodo archive}
\label{sec:zenodo-archive}

The submission snapshot is frozen as a Git tag, published as a GitHub release, and archived by Zenodo, which mints a citable DOI for the snapshot.

\begin{quote}
Archived obstruction-bridge snapshot:
Zenodo version DOI
\url{https://doi.org/10.5281/zenodo.20796920}
for tag
\code{papers-m2-v2-obstruction-bridge}
at commit
\code{d7e5fd1ac94ab18330951b5d9741585dddc5b43a}.
The Zenodo record belongs to concept DOI
\url{https://doi.org/10.5281/zenodo.20468649}.
\end{quote}

The version DOI, Git tag, and exact commit jointly identify the archived
Stage~3 source snapshot. The DOI reference in this appendix was recorded after
the release was published and therefore does not move or alter the archived
tag. The prior DOI \url{https://doi.org/10.5281/zenodo.20468650} identifies the
superseded pre-bridge \code{papers-m2-v1} snapshot.

\subsection{Build commands}
\label{sec:build-commands}

The narrow build commands that exercise the bridge and compatibility theorem are:
\begin{quote}
\code{lake env lean SocialChoiceAtlas/Sen/ObstructionBridge.lean}
\end{quote}
\begin{quote}
\code{lake env lean SocialChoiceAtlas/Sen/Lifting/ImpossibilityLift.lean}
\end{quote}

The M2 smoke gate is:
\begin{quote}
\code{./scripts/ci\_m2\_smoke.sh}
\end{quote}

The full default kernel build is:
\begin{quote}
\code{lake build}
\end{quote}

The manuscript itself builds with:
\begin{quote}
\code{make -C papers/m2 pdf}
\end{quote}

\subsection{Artifact binding}
\label{sec:artifact-binding}

\begingroup
\renewcommand{\arraystretch}{1.15}
\noindent\begin{tabularx}{\linewidth}{@{}>{\raggedright\arraybackslash}p{0.36\linewidth} >{\raggedright\arraybackslash}X@{}}
\toprule
Claim & Binding \\
\midrule
Witness extraction and classification & \code{SocialChoiceAtlas/Sen/ObstructionBasis.lean} \\
Generic profile construction & \code{SocialChoiceAtlas/Sen/ObstructionProfiles.lean} \\
Shape soundness and exact cardinalities & \code{SocialChoiceAtlas/Sen/ObstructionSoundness.lean} \\
Theorem~\ref{thm:bridge} (generic outcome bridge) & \code{SocialChoiceAtlas/Sen/ObstructionBridge.lean} (\texttt{sen\_outcome\_obstruction\_}\allowbreak\texttt{of\_UN\_MINLIB}) \\
Theorem~\ref{thm:generic-impossibility} (generic impossibility) & \code{SocialChoiceAtlas/Sen/ObstructionBridge.lean} (\texttt{sen\_impossibility\_}\allowbreak\texttt{from\_obstruction\_basis}) \\
Corollary~\ref{thm:lift} (legacy compatibility theorem) & \code{SocialChoiceAtlas/Sen/Lifting/ImpossibilityLift.lean} (\texttt{sen\_impossibility\_lifts}) \\
Default kernel build & \code{SocialChoiceAtlas.lean} (root imports) \\
M2 smoke gate & \code{scripts/ci\_m2\_smoke.sh} \\
Proposition~\ref{prop:scope-wall} (scope wall) & \code{docs/m2\_scope\_wall.md} \\
Short-cycle scaling note & \code{docs/no\_cycle\_interpretation\_note.md} \\
Axiom-semantics scaling note & \code{docs/axiom\_semantics\_scaling.md} \\
\bottomrule
\end{tabularx}
\endgroup

\paragraph{What is not part of this reproduction.}
No new solver runs are part of this paper.
No new CNF, LRAT, atlas, or repair artifacts are generated for M2.
The representation-canonicity question at family scale is deferred to a companion paper (in preparation); its reproduction record will be authored alongside that paper, not here.
