\section{Methods}

\subsection{Atlas enumeration}
We enumerate axiom subsets over a fixed universe and solve each case to obtain SAT/UNSAT status.
Outputs include per-case CNF/manifest/summary and top-level \code{atlas.json}.

\subsection{Boundary extraction}
For UNSAT solved cases, we run a deletion-based MUS procedure and a small MCS search (single removals first, then bounded pairs).
This is intentionally the narrow C2 claim: one MUS and one small MCS candidate are enough to explain the boundary case without claiming full repair enumeration.

\subsection{Repair enumeration and triangulation}
When we want the stronger C6 evidence, we run a separate post-processing stage with \code{scripts/enumerate_repairs.py} and \code{scripts/triangulate_repairs.py}.
The paper keeps this distinct from C2 so that repair \emph{enumeration} is not confused with boundary \emph{explanation}.

\subsection{Proof-carrying UNSAT policy}
For canonical UNSAT references, we retain CNF+LRAT and verify in Lean.
For atlas runs, proof metadata is recorded with hash-based linkage and replay commands.

\subsection{sen24 acyclicity boundary}
The CNF does not encode Lean's \code{Acyclic} predicate directly. Instead, for sen24 it forbids directed 3-cycles and 4-cycles.
We therefore add one explicit finite check to the method: \code{scripts/check_acyclicity_short_cycles.py} exhaustively enumerates the four-alternative relation space and verifies that, under asymmetry, this short-cycle encoding is equivalent to acyclicity.
This is a sen24-specific audited fact, not a scalability claim.

\subsection{SAT Gallery with witness validation}
SAT cases are filtered by lightweight non-trivial heuristics and ranked deterministically.
Each selected witness is validated against CNF using a solver-independent checker that parses DIMACS and model assignments directly.
