\section{Verification Status and Evidence Accounting}

This section is organized as a claim-by-claim evidence checklist rather than a fresh benchmark report.
The goal of the current revision is to state, for each official claim C1--C6, which artifact supports it and what was actually re-verified now.
The runtime harness in \texttt{scripts/eval\_atlas.py} was re-run at smoke scope inside \texttt{./scripts/ci\_phase2\_smoke.sh}, but it is used here only as a sanity check on metadata and plotting, not as a new performance claim.
The sen24 short-cycle/acyclicity bridge is tracked separately as an audited finite Python check, not as a Lean-side proof obligation under C1--C6.

\paragraph{C1: reproducible frontier generation.}
Primary support comes from \texttt{scripts/run\_atlas.py}, \texttt{atlas.json}, \texttt{atlas\_summary.md}, and per-case \texttt{summary.json}.
This revision re-verified C1 through \texttt{./scripts/ci\_phase2\_smoke.sh}, which re-runs a full 32-case sen24 atlas in the repair smoke path and checks the resulting frontier artifacts.

\paragraph{C2: one MUS and one small MCS candidate.}
Primary support comes from \texttt{scripts/mus\_mcs.py} and the embedded \texttt{mus}/\texttt{mcs} fields in \texttt{atlas.json}.
This revision re-verified the smoke-scope version of C2 through \texttt{./scripts/ci\_phase2\_smoke.sh}, which regenerates \texttt{mus.json} and \texttt{mcs.json} for the committed UNSAT boundary case \texttt{case\_11111}.

\paragraph{C3: committed proof-carrying UNSAT.}
Primary support comes from the committed reference \texttt{Certificates/atlas/case\_11111/\{sen24.cnf,proof.lrat\}}, the Lean target \texttt{SocialChoiceAtlas.Sen.Atlas.Case11111}, and proof metadata in regenerated summaries.
This revision re-verified C3 through both \texttt{./scripts/ci\_phase1.sh} and \texttt{./scripts/ci\_phase2\_smoke.sh}, which rebuild Lean proof targets and check the committed proof-carrying case.

\paragraph{C4: guarded symmetry reduction and monotone pruning.}
Primary support comes from \texttt{docs/assumptions\_monotone\_pruning.md}, \texttt{docs/safety\_symmetry\_reduction.md}, and the runtime guardrail fields in \texttt{atlas.json}.
This revision re-verified C4 through \texttt{./scripts/ci\_phase2\_smoke.sh}, which executes both symmetry-checked and prune-checked atlas runs and validates their metadata.

\paragraph{C5: auditable SAT gallery.}
Primary support comes from \texttt{scripts/build\_sat\_gallery.py}, \texttt{gallery.json}, \texttt{gallery.md}, per-case \texttt{rule\_card.md}/\texttt{rule\_card.tex}, and embedded SAT witness-validation statistics.
This revision re-verified C5 through \texttt{./scripts/ci\_phase2\_smoke.sh}, which rebuilds a small gallery, checks that selected entries are non-trivial and validated, and confirms that rule-card artifacts exist.

\paragraph{C6: repair triangulation against an independent optimum baseline.}
Primary support comes from \texttt{scripts/enumerate\_repairs.py}, \texttt{scripts/triangulate\_repairs.py}, \texttt{repair\_triangulation.json}, and the comparison fields \texttt{size\_match}/\texttt{set\_match}.
This revision re-verified C6 through \texttt{./scripts/ci\_phase2\_smoke.sh}, which re-runs full repair enumeration and triangulation on a solved 32-case sen24 atlas.
