\section{Related Work and Positioning}

The closest prior context is SAT-based computational social choice.
That line already showed that SAT solving can be used to prove impossibility results, search for axiomatizations, and discover proofs in small finite domains; it includes the style associated with Tang and Lin, later automated exploration and proof discovery by Geist and Endriss \citep{geist2011automated}, and MUS-oriented explanation work associated with Brandt and Geist.
Our paper does not claim novelty for ``using SAT in social choice,'' for extracting contradictions, or for small-scope automated theorem search by itself.
Its narrower contribution is to package one fixed sen24 search workflow as an explicit auditable contract whose outputs are replayable artifacts rather than solver conclusions alone.

This difference is about contract structure, not theorem content.
Prior COMSOC-SAT work is the direct intellectual predecessor for boundary search and explanation, and we build squarely on that perspective.
What we add is a paper-level separation between proof, audit, and assumption: semantic Lean theorems on one side, manifest-audited CNF artifacts in the middle, committed LRAT replay for reference UNSAT cases, and independently validated SAT witnesses for displayed feasible rules.
In that sense, the paper is closer to certificate-backed automated reasoning than to a new impossibility proof technique.

Certificate checking and proof-carrying automated reasoning form the second comparison point.
We differ from that tradition not by stronger proof checking, but by the way it is embedded into a social-choice workflow.
The central artifact is not a bare proof trace: it is an auditable atlas with a reproducible frontier, one MUS and one small MCS candidate for boundary explanation, committed proof-carrying UNSAT references, validated SAT rule cards, stronger repair triangulation as a separate stage, and explicit commands and hashes for replay.
The value of the package is that a reviewer can inspect where kernel-checked proof ends, where mechanical auditing begins, and where assumptions remain.

Constraint Hierarchies, ATMS, MAXSAT, and OMT remain relevant only as secondary contrasts.
They reason about conflicting constraints, consistency under assumptions, or optimal relaxations, and they are useful reference points for the repair side of the story.
But this paper does not position itself as a replacement for them or as a speed comparison against them.
Their role here is narrower: optimization-style reasoning appears as the independent triangulation baseline for C6, whereas the main contribution remains auditable boundary mapping, conservative MUS/MCS explanation, and replayable SAT/UNSAT evidence artifacts.

The scope is intentionally narrow.
We claim only a sen24 case study under a small-scope hypothesis, not a general account of arbitrary $n,m$, not completeness for multiple theorem families, and not formal Lean verification of symmetry or pruning heuristics.
The point is that even under those limits, the paper makes one JAR-relevant contribution precise: a small social-choice impossibility search can be presented as an auditable reasoning workflow with a visible trust contract.
