\section{Introduction}
\label{sec:introduction}

\paragraph{Motivation.}
Classical social-choice impossibility results name semantic axioms as the
units of explanation: \(\mathtt{UN}\), \(\mathtt{MINLIB}\), \(\mathtt{IIA}\),
and related labels are the terms in which the theorem is stated and debated.
Computational implementations may not preserve that granularity.  A single
semantic axiom can be split into several implementation levers, and repairs
computed over those levers need not arrive already packaged in the axiom-level
language used in a human-facing report.  This is not unique to social choice,
but it is particularly consequential in computational social choice because
axiom names themselves are the theoretical and normative units of discussion.

Auditable finite-atlas evidence can certify the truth/certificate side of the
story: which residual cases were generated, solved, and checked.  It does not
automatically justify the level at which repairs are reported.  M1 established
an auditable finite-atlas workflow separating Proof, Audit, Witness, and
Assumption obligations.  M1.5 then showed the negative repair-reporting fact:
even clause-multiset equivalence does not force the raw repair family to be
canonical.  Truth/certificate validity does not determine repair-reporting
granularity.

M3 asks the positive follow-up question:
\begin{quote}
\emph{When may a representation-sensitive implementation repair be reported at
a declared axiom-level contract interface?}
\end{quote}
When the paper uses report-correct or faithful language, it means
contract-relative report correctness, not semantic truth, normative truth, or a
claim about which repair should be selected.

\paragraph{Thesis.}
A valid impossibility certificate does not determine a valid repair report.
Reportability is contract-relative: the paper must say which contract atoms
are reportable, how implementation levers map to those atoms, and why grouped
reports preserve the reference residual semantics.  M3 does not determine
which repair should be chosen.  It characterizes when distinct
implementation-level repairs may be reported at a common axiom-level contract
interface without changing the declared contract repair family.
Candidate B supplies the motivating artifact-defined instantiation.

\begin{figure}[t]
  \centering
  \resizebox{\textwidth}{!}{%
  \begin{tikzpicture}[
      >=Stealth,
      stage/.style={draw, rounded corners, align=center, minimum width=2.8cm,
        minimum height=1.15cm, font=\small},
      rawstage/.style={stage, fill=red!8, draw=red!60!black},
      theorystage/.style={stage, fill=blue!7, draw=blue!55!black},
      auditstage/.style={stage, fill=green!8, draw=green!45!black},
      arrow/.style={->, thick}
    ]
    \node[rawstage] (m15) {M1.5\\Raw repair\\non-canonicity};
    \node[theorystage, right=0.9cm of m15] (m3a) {M3-A\\Atomic sufficient\\condition};
    \node[theorystage, right=0.9cm of m3a] (m3b) {M3-B\\Non-atomic\\\(\GroupSoundness\)};
    \node[theorystage, right=0.9cm of m3b] (m3c) {M3-C\\Monotone\\exactness};
    \node[auditstage, right=0.9cm of m3c] (cb) {Candidate B\\Raw-noncanonical\\grouped report-correct};

    \draw[arrow] (m15) -- (m3a);
    \draw[arrow] (m3a) -- (m3b);
    \draw[arrow] (m3b) -- (m3c);
    \draw[arrow] (m3c) -- (cb);

    \node[font=\scriptsize, text=red!60!black, above=0.35cm of m15]
      {negative raw-level result};
    \node[draw=blue!45!black, dashed, rounded corners,
      fit=(m3a)(m3b)(m3c), inner xsep=0.18cm, inner ysep=0.35cm,
      label={[font=\scriptsize, text=blue!55!black]above:positive contract-level theory}] {};
  \end{tikzpicture}}
  \caption{The paper spine separates the negative raw-level result from the
  positive contract-level theory.}
  \label{fig:spine}
\end{figure}

\paragraph{Contributions and boundary.}
The paper does not claim novelty for the broad phenomenon that MUS, MCS, or
repair families can vary with representation.  That sensitivity is part of the
background diagnosis and repair-enumeration landscape.  The positive
contribution is to theoremize when such low-level variation may be reported
through a higher-level contract interface without changing the reference repair
family:
\begin{enumerate}[label=(\roman*)]
  \item explicit reportability contracts;
  \item M3-A, an atomic syntactic sufficient condition;
  \item M3-B, a non-atomic \(\GroupSoundness\) condition;
  \item M3-C, a monotone-regime characterization of \(\GroupSoundness\) by
    pointwise grouped correctness for residually faithful realizations;
  \item a kernel-checked finite counterexample showing that the monotonicity
    assumption in M3-C is necessary;
  \item a Lean-checked abstract finite-set theorem core; and
  \item a Candidate B artifact-backed instantiation of M3-B.
\end{enumerate}

The theorem core is not only stated in Lean syntax; the listed declarations
are closed in the compiled Lean development.

M3-B establishes grouped report correctness on Candidate B only after the
reportability contract is made explicit and both \(\ResidualFaithfulness\) and
\(\GroupSoundness\) are verified.
It does not erase M1.5, make raw repairs canonical, or make M3-A applicable to
the non-atomic Candidate B realization.

Concretely, the split encoding exposes two distinct person-indexed singleton
repairs,
\(\{\mathtt{decisive\_voter0}\}\) and
\(\{\mathtt{decisive\_voter1}\}\).  Under the declared artifact-defined
bundled contract, touch-any grouping maps both to
\(\{\mathtt{minlib}\}\).  M3-B establishes that the resulting grouped repair
predicate coincides pointwise with the contract repair predicate.  Thus
\(\{\mathtt{minlib}\}\) is a report-correct grouped label under this contract;
it is neither the unique nor the normatively preferred repair.

\paragraph{Claim discipline.}
Table~\ref{tab:claim-discipline} records the qualifications that govern the
manuscript.

\begin{table}[t]
\centering
\scriptsize
\begin{tabularx}{\textwidth}{@{}p{0.32\textwidth}p{0.08\textwidth}X@{}}
\toprule
Claim & Allowed? & Required qualification \\
\midrule
M1.5 shows raw repair non-canonicity & yes & Candidate B / declared artifact scope \\
M3-A recovers Candidate B & no & M3-A does not apply to non-atomic split \code{minlib} \\
M3-B establishes grouped report correctness on Candidate B & yes & only under artifact-defined contract and verified \(\ResidualFaithfulness\) plus \(\GroupSoundness\) \\
Candidate B raw repairs become canonical & no & raw non-canonicity remains \\
\(\mathtt{minlib}\) is the unique or preferred repair & no & M3 characterizes report correctness, not repair selection or ranking \\
\(\GroupSoundness\) characterizes grouped correctness & yes & only for residually faithful realizations over \(\Psi\)-deletion-monotone contracts \\
Atomicity is necessary & no & M3-A is a sufficient condition only \\
Raw transport holds under M3-B & no & raw transport is an M3-A result only \\
M3 results extend to family scale & no & Candidate B is artifact-defined / base-scope unless separately lifted \\
Arrow provides a second M3 example & no & Arrow is a prerequisite testbed unless per-residual transfer is established \\
Artifact-defined contract equals semantic/Lean contract & no & semantic/formal upgrading is a separate truth/certificate obligation \\
Encoding-granularity sensitivity of repairs is new by itself & no & M3's novelty is contract-relative reportability and exactness conditions \\
\bottomrule
\end{tabularx}
\caption{Claim discipline for the M3 paper.}
\label{tab:claim-discipline}
\end{table}

\paragraph{Paper organization.}
Section~\ref{sec:contracts} defines contracts and repair predicates.
Sections~\ref{sec:atomic}--\ref{sec:monotone} state M3-A, M3-B, and M3-C.
Section~\ref{sec:candidate-b} records the artifact-backed instantiation.
Sections~\ref{sec:related}--\ref{sec:discussion} position and delimit the result.
Exact Lean signatures and artifact audit tables appear in the appendices.
