\section{Atomic Interfaces}
\label{sec:atomic}

Atomicity gives the simplest sufficient condition for reportability.  If each
active contract atom has exactly one active lever, then every subset of the
active lever interface is block-aligned.  Pairwise block disjointness yields
the complement identity, and residual faithfulness transfers feasibility and
minimality between the implementation and contract domains.

\begin{theorem}[M3-A: atomic grouped correctness]
\label{thm:m3a}
Assume active blocks are pairwise disjoint.  If \(\RepairAtomicity\) and
\(\ResidualFaithfulness\) hold, then for every contract deletion \(G\),
\[
  \GroupedRepair(G)
  \quad\Longleftrightarrow\quad
  \ContractRepair(G).
\]
\end{theorem}

The Lean declaration is \code{m3a_grouped_correctness}.  The proof factors
through the following finite-set steps.

\paragraph{Complement identity.}
For \(G\subseteq I\), pairwise disjointness gives
\[
  \betaSet(I\setminus G)
  =
  \Lambda_I\setminus\betaSet(G).
\]
This identity does not use atomicity.  It records that retaining the blocks
outside \(G\) is the same as removing the block image of \(G\) from the active
lever interface.

\paragraph{Atomic block alignment.}
Under atomicity, every \(R\subseteq\Lambda_I\) is
\(\betaSet(G)\) for a unique \(G\subseteq I\).  Existence follows because each
active lever belongs to a singleton active block; uniqueness uses the
atom-indexed block map together with disjointness and the nonemptiness supplied
by atomicity.  This is the step at which atomicity is essential: it ensures
that arbitrary implementation deletions, not merely chosen block deletions,
are block-aligned.

\paragraph{Feasibility transfer.}
The complement identity rewrites an implementation residual after deleting
\(\betaSet(G)\) as the retained block residual
\(\betaSet(I\setminus G)\).  Residual faithfulness then yields
\[
  \SatPhi(\Lambda_I\setminus\betaSet(G))
  \quad\Longleftrightarrow\quad
  \SatPsi(I\setminus G).
\]
Thus block-aligned raw feasibility and contract feasibility agree.

\paragraph{Minimality transfer.}
The same correspondence transfers inclusion-minimality.  A smaller contract
deletion maps to a smaller block deletion, and atomic block alignment sends
every raw-feasible subdeletion back to an active atom set.  Consequently,
\(\RawRepair(\betaSet(G))\) holds exactly when
\(\ContractRepair(G)\) holds.

\paragraph{Grouping and pointwise correctness.}
For every \(G\subseteq I\),
\[
  \groupTouchAny(\betaSet(G))=G.
\]
This grouping identity uses disjointness and nonempty blocks only; it does not
use atomicity.  Atomicity has already ensured that every raw repair has the
form \(\betaSet(G)\).  The raw-repair correspondence and grouping identity
therefore identify the occurring grouped image with the contract-repair
family, whose inclusion-minimal elements are unchanged.  This proves the
pointwise equivalence in Theorem~\ref{thm:m3a}.

\begin{corollary}[Atom-indexed raw transport]
\label{cor:m3a-raw}
For two atomic, residually faithful realizations of the same contract, and for
every \(G\subseteq I\), the block deletion induced by \(G\) is a raw repair in
the first realization if and only if the block deletion induced by \(G\) is a
raw repair in the second.
\end{corollary}

This is the Lean theorem \code{m3a_raw_transport}.  It is atom-indexed rather
than an arbitrary lever-bijection theorem.

\paragraph{Limit.}
Atomicity is sufficient, not necessary.  M3-A does not apply to Candidate B
because
\[
  \beta(\mathtt{minlib})
  =
  \{\mathtt{decisive\_voter0},\mathtt{decisive\_voter1}\}
\]
is non-atomic.  Raw transport is an M3-A result only and must not be attributed
to M3-B.

\paragraph{Dependency record.}
Appendix~\ref{app:lean} includes the exact theorem signatures, the
paper-to-Lean correspondence map, and a compact record of where atomicity is
and is not used.
