\section{Non-Atomic Group Soundness}
\label{sec:group-soundness}

M3-B permits non-atomic blocks and therefore permits partial-block deletions.
The replacement for syntactic block alignment is a semantic reporting
condition: every feasible implementation deletion must remain feasible in the
reference contract after touch-any grouping.

\begin{theorem}[M3-B: non-atomic grouped correctness]
\label{thm:m3b}
Assume active blocks are pairwise disjoint.  If
\(\ResidualFaithfulness\) and \(\GroupSoundness\) hold, then for every grouped
deletion \(G\),
\[
  \GroupedRepair(G)
  \quad\Longleftrightarrow\quad
  \ContractRepair(G).
\]
\end{theorem}

The statement is pointwise predicate equivalence, not an unqualified function
equality.  The Lean declaration is \code{m3b_grouped_correctness}.

\paragraph{B1: contract repairs occur in the grouped raw image.}
Let \(G\) be a contract repair.  Residual faithfulness and the block-complement
identity make \(\betaSet(G)\) a feasible implementation deletion.  Finite
descent then chooses a raw minimal subdeletion
\(R_0\subseteq\betaSet(G)\) from this already feasible deletion.  This descent
uses finiteness only and does not assume deletion-monotonicity of \(\SatPhi\).
Disjointness implies
\(\groupTouchAny(R_0)\subseteq G\); group soundness makes that grouped deletion
contract-feasible; and contract minimality forces
\(\groupTouchAny(R_0)=G\).  Hence \(G\) occurs in the grouped raw image.

\paragraph{B2: grouped raw reports are contract-feasible.}
For a raw repair \(R\), raw feasibility supplies
\(\SatPhi(\Lambda_I\setminus R)\).  Applying \(\GroupSoundness\) gives
\(\SatPsi(I\setminus\groupTouchAny(R))\), while the filtering definition of
touch-any grouping ensures \(\groupTouchAny(R)\subseteq I\).  Thus every
grouped raw report is a contract-feasible deletion.

\paragraph{B3: grouped raw reports contain contract repairs.}
Given a member \(G\) of the grouped raw image, B2 makes \(G\)
contract-feasible.  A second finite descent, now inside \(G\), selects a
contract-minimal feasible subset \(G_0\subseteq G\).  Therefore every grouped
raw report contains at least one contract repair, even when the originating
raw repair deletes only part of an implementation block.

\paragraph{B4: minimizing the grouped image gives exactly contract repairs.}
B1 places every contract repair in the grouped raw image.  B3 places a
contract repair below every member of that image.  Inclusion-minimality on
both sides then gives
\(\GroupedRepair(G)\leftrightarrow\ContractRepair(G)\) pointwise.  M3-B thus
permits partial-block deletion, but requires it to remain sound after
grouping.  Its conclusion is grouped correctness only, not raw transport.

\begin{corollary}[Two realizations]
If two realizations of the same reference contract are residually faithful and
group-sound, their grouped repair predicates are pointwise equivalent through
the common contract repair predicate.
\end{corollary}

This corollary is implemented as \code{m3b_two_realization}.  M3-B establishes
grouped correctness, not raw transport.

\paragraph{Candidate B qualification.}
The Candidate B use of M3-B relies on complete artifact-level raw-repair
enumeration and grouped-image verification; the Lean theorem proves the
abstract sufficient condition, not the artifact enumeration.
