\section{Exactness under Monotone Contracts}
\label{sec:monotone}

\(\PsiDeletionMonotonicity\) says that deleting more contract atoms cannot
destroy reference feasibility.  This is natural for standard conjunctive
axiom-deletion contracts, where deleting an atom removes constraints, but it is
not assumed for arbitrary reportability contracts.

\begin{theorem}[M3-C: monotone converse]
\label{thm:m3c}
If \(\PsiDeletionMonotonicity\) holds and grouped correctness holds pointwise,
\[
  \forall G,\quad
  \GroupedRepair(G)\leftrightarrow\ContractRepair(G),
\]
then \(\GroupSoundness\) holds.
\end{theorem}

The Lean declaration \code{m3c_converse} does not assume residual faithfulness.
To prove the converse, begin with an arbitrary feasible implementation
deletion and descend to a raw minimal subdeletion.  Its touch-any image belongs
to the grouped raw image, so finite descent inside that image produces a
minimal grouped report below it.  Pointwise grouped correctness identifies
this report as a contract repair.  Since the contract repair's grouped
deletion is contained in the original grouped deletion, the retained residual
for the original deletion contains no more contract atoms; reference
deletion-monotonicity transfers feasibility to it and establishes
\(\GroupSoundness\).

Residual faithfulness is absent because this direction never compares a
block-aligned implementation residual with a reference residual.  It starts
from the assumed grouped-correctness predicate, extracts a contract repair,
and uses only \(\PsiDeletionMonotonicity\) to reach the required reference
feasibility statement.

\begin{corollary}[Exactness]
\label{cor:exactness}
For a residually faithful realization with pairwise disjoint active blocks over
a \(\Psi\)-deletion-monotone contract,
\[
  \GroupSoundness
  \quad\Longleftrightarrow\quad
  \forall G,\
  \GroupedRepair(G)\leftrightarrow\ContractRepair(G).
\]
\end{corollary}

This is \code{groupSoundness_iff}.  Residual faithfulness is used in the M3-B
forward direction: group soundness plus residual faithfulness yields grouped
correctness.  The reverse direction is M3-C: grouped correctness plus
\(\PsiDeletionMonotonicity\) yields group soundness without residual
faithfulness.  The equivalence is therefore scoped to residually faithful
realizations over deletion-monotone reference contracts, not arbitrary
reportability contracts.  Standard conjunctive axiom-deletion contracts
provide the motivating intuition because removing an atom removes
constraints; the theorem itself uses the stated monotonicity predicate.

\begin{proposition}[Audit-cost collapse]
\label{prop:audit-collapse}
Under \(\PsiDeletionMonotonicity\), if every raw minimal repair \(R\) satisfies
\[
  \SatPsi(I\setminus\groupTouchAny(R)),
\]
then unrestricted \(\GroupSoundness\) holds.
\end{proposition}

The Lean declaration is \code{audit_cost_collapse}.  Its finite descent does
not assume deletion monotonicity of \(\SatPhi\).  From an arbitrary feasible
deletion \(R\), it selects a raw repair \(R_0\subseteq R\).  Touch-any grouping
is monotone, so
\(\groupTouchAny(R_0)\subseteq\groupTouchAny(R)\).  The assumed reference
check for \(R_0\), followed by \(\PsiDeletionMonotonicity\), therefore proves
the grouped reference residual feasible for \(R\).  Checking all raw minimal
repairs is sufficient for unrestricted group soundness precisely because the
finite descent and grouped monotonicity cover every feasible deletion.

The monotonicity assumption is not removable.  The compiled finite example in
\code{Examples.lean} has pointwise grouped correctness but fails both
\(\GroupSoundness\) and \(\PsiDeletionMonotonicity\).  Thus grouped correctness
alone does not imply group soundness in a non-monotone reference contract.

\paragraph{Comparison.}
Table~\ref{tab:theorem-comparison} separates the roles of the three theorem
components.

\begin{table}[t]
\centering
\scriptsize
\begin{tabularx}{\textwidth}{@{}p{0.07\textwidth}p{0.20\textwidth}p{0.20\textwidth}p{0.27\textwidth}p{0.08\textwidth}X@{}}
\toprule
Component & Interface / soundness condition & Other assumptions & Conclusion & Raw transport? & Lean status \\
\midrule
M3-A & \(\RepairAtomicity\) & block disjointness; \(\ResidualFaithfulness\) & pointwise grouped correctness & yes, atom-indexed & checked \\
M3-B & \(\GroupSoundness\) & block disjointness; \(\ResidualFaithfulness\) & pointwise grouped correctness; two-realization corollary & no & checked \\
M3-C & pointwise grouped correctness & \(\PsiDeletionMonotonicity\) & \(\GroupSoundness\) & no & checked \\
\bottomrule
\end{tabularx}
\caption{M3-A, M3-B, and M3-C have different logical roles.}
\label{tab:theorem-comparison}
\end{table}
