\section{Candidate B: Artifact-Backed Instantiation}
\label{sec:candidate-b}

This section instantiates M3-B using existing artifacts; it is not a Lean
formalization of those artifacts.  The bundled artifact-defined contract is
\[
  I =
  \{\mathtt{asymm},\mathtt{un},\mathtt{minlib},\mathtt{no\_cycle4}\}.
\]
The \(\mathtt{no\_cycle3}\) lever is inactive in this contract scope.  The split
implementation refines the liberalism block as
\[
  \beta(\mathtt{minlib})
  =
  \{\mathtt{decisive\_voter0},\mathtt{decisive\_voter1}\}.
\]
Candidate B is therefore non-atomic and falls under M3-B rather than M3-A.

\paragraph{Audit provenance.}
The M3 Candidate B audit is artifact-only; no new solver run is part of this
paper audit.  The main audit record is
\code{docs/m3_candidate_b_group_soundness_audit_result.md}, and the main
structured comparison artifact is
\code{results/20260401/candidate_b_minlib_granularity/comparison.json}.
The fully active bundled case is
\code{bundled/case_11101}, and the fully active split case is
\code{split/case_111101}.  Throughout this instantiation,
\code{no_cycle3} is fixed inactive.  The audit therefore establishes M3-B
only inside the bundled artifact-defined contract declared above.

\begin{figure}[t]
  \centering
  \resizebox{0.96\textwidth}{!}{%
  \begin{tikzpicture}[
      >=Stealth,
      atom/.style={draw, rounded corners, align=center, minimum width=2.7cm,
        minimum height=0.95cm, fill=blue!7, draw=blue!55!black, font=\small},
      lever/.style={draw, rounded corners, align=center, minimum width=3.1cm,
        minimum height=0.95cm, fill=orange!9, draw=orange!70!black, font=\small},
      raw/.style={draw, rounded corners, align=center, minimum width=3.1cm,
        minimum height=0.95cm, fill=red!7, draw=red!60!black, font=\small},
      report/.style={draw, rounded corners, align=center, minimum width=2.7cm,
        minimum height=0.95cm, fill=green!8, draw=green!45!black, font=\small},
      arrow/.style={->, thick}
    ]
    \node[atom] (minlib) {bundled atom\\\(\mathtt{minlib}\)};
    \node[lever, below left=1.15cm and 0.45cm of minlib] (dv0)
      {split lever\\\(\mathtt{decisive\_voter0}\)};
    \node[lever, below right=1.15cm and 0.45cm of minlib] (dv1)
      {split lever\\\(\mathtt{decisive\_voter1}\)};
    \node[raw, below=1.1cm of dv0] (r0)
      {raw repair\\\(\{\mathtt{decisive\_voter0}\}\)};
    \node[raw, below=1.1cm of dv1] (r1)
      {raw repair\\\(\{\mathtt{decisive\_voter1}\}\)};
    \node[report, below=2.55cm of minlib] (grp)
      {grouped report\\\(\{\mathtt{minlib}\}\)};

    \draw[arrow, orange!70!black] (minlib) -- node[left, font=\scriptsize]
      {\(\beta\)} (dv0);
    \draw[arrow, orange!70!black] (minlib) -- node[right, font=\scriptsize]
      {\(\beta\)} (dv1);
    \draw[arrow, red!60!black] (dv0) -- (r0);
    \draw[arrow, red!60!black] (dv1) -- (r1);
    \draw[arrow, green!55!black] (r0) -- node[left, font=\scriptsize]
      {\(\groupTouchAny\)} (grp);
    \draw[arrow, green!55!black] (r1) -- node[right, font=\scriptsize]
      {\(\groupTouchAny\)} (grp);

    \node[atom, left=1.45cm of grp] (aligned)
      {\(\{\mathtt{asymm}\}\), \(\{\mathtt{un}\}\),\\
       \(\{\mathtt{no\_cycle4}\}\)\\singleton-aligned};
    \node[font=\scriptsize, align=center, below=0.12cm of aligned]
      {reported unchanged};
  \end{tikzpicture}}
  \caption{Raw split repairs remain distinct while their contract report is
  shared.}
  \label{fig:candidate-b}
\end{figure}

\paragraph{Evidence sources.}
\begin{description}[style=nextline,leftmargin=2.9cm]
  \item[Fully active UNSAT.]
    Bundled \code{case_11101} and split \code{case_111101}.
  \item[Residual faithfulness.]
    The 16 block-aligned rows in \code{comparison.json}, all filtered to
    \code{no_cycle3=off}.
  \item[RawRep completeness.]
    The five split singleton repairs are
    \[
      \begin{gathered}
      \{\mathtt{asymm}\},\ \{\mathtt{un}\},\
      \{\mathtt{decisive\_voter0}\},\\
      \{\mathtt{decisive\_voter1}\},\
      \{\mathtt{no\_cycle4}\}.
      \end{gathered}
    \]
    Fully active UNSAT and the singleton-dominance argument are recorded in
    the audit result.
  \item[GroupSoundness checks.]
    All five grouped raw repairs map to bundled SAT residuals.
  \item[\(\Psi\)-deletion monotonicity.]
    The complete 16-row bundled lattice records the fully active residual
    UNSAT and every proper residual SAT.
  \item[No new solver run.]
    The completed audit reuses the recorded Candidate B artifacts.
\end{description}

\paragraph{What would invalidate the instantiation.}
Candidate B would no longer instantiate M3-B under this contract if either
fully active residual were not UNSAT; any block-aligned comparison failed; the
split raw-repair family were incomplete; a non-singleton or missing singleton
changed the RawRep completeness claim; any grouped raw repair failed to map to
a bundled SAT residual; \(\PsiDeletionMonotonicity\) failed on the bundled
16-row lattice; \code{no_cycle3} were silently treated as active; or the
artifact-defined contract were silently upgraded to semantic or Lean-level
status.

\paragraph{Why the artifact-defined instantiation is non-circular.}
The bundled residual predicate defines the artifact-level reference contract,
but the M3-B instantiation is not automatic from that definition.  The
nontrivial checked fact is that the split raw-repair family, after touch-any
grouping and minimization, coincides with the bundled contract repair family.
This requires three verified ingredients: residual faithfulness across all 16
block-aligned residuals; complete split \(\RawRepair\) enumeration; and
\(\GroupSoundness\) via audit-cost collapse over the bundled monotone lattice.
The Candidate B result is therefore a structural agreement between raw
implementation repairs and grouped contract reports, not a circular restatement
of the bundled contract.  The agreement is triangulated both by the abstract
M3-B theorem and by the direct artifact tables in Appendix~\ref{app:audit}.

Given the complete artifact-level enumeration of the split raw repairs,
Proposition~\ref{prop:audit-collapse} turns the grouped SAT checks into
unrestricted \(\GroupSoundness\).  Residual faithfulness is supplied by the 16
block-aligned status comparisons.  Therefore:

\paragraph{Result (Candidate B instantiation).}
Candidate B instantiates M3-B under the bundled-level artifact-defined
contract.

The grouped family is
\[
  \bigl\{
  \{\mathtt{asymm}\},
  \{\mathtt{un}\},
  \{\mathtt{minlib}\},
  \{\mathtt{no\_cycle4}\}
  \bigr\}.
\]

Candidate B is raw-noncanonical and contract-canonical at the same time.
This does not upgrade the artifact-defined contract to a semantic or
Lean-level contract.  That upgrade is a separate truth/certificate obligation.
