\section{Related Work and Positioning}
\label{sec:related}

\paragraph{Model-based diagnosis and ATMS.}
Assumption-based truth maintenance and model-based diagnosis provide the
background vocabulary for conflicts, assumptions, and repairs
\citep{dekleer1986atms,reiter1987}.  Constraint hierarchies address conflict
resolution under prioritized constraints \citep{borning1992constraint}.
This paper uses this repair vocabulary but studies a different obligation: when an
implementation-level deletion may be reported at a declared contract interface.
The contract is not merely a display convention.  It specifies the reportable
atoms and the residual semantics that the grouped report must preserve.  This
paper differs from diagnosis-style grouping in treating the grouping interface as a
residual-semantics preservation obligation: a raw deletion may be reported as a
contract deletion only when residual faithfulness and the relevant interface
condition, atomicity or \(\GroupSoundness\), justify that report.

\paragraph{MUS/MCS and repair enumeration.}
Minimal conflict and correction-set techniques, together with MaxSAT-style
repair search, establish that explanation families depend on the chosen
constraint representation \citep{li2009maxsat}.  We therefore do not claim
novelty for the observation that MUS or repair sets change under encoding
granularity.  Prior diagnosis and repair work establishes that explanations
depend on the representation of constraints.  This paper addresses a different
obligation: when a representation-sensitive implementation repair may
nevertheless be reported at a higher-level contract interface without changing
the reference repair family.  Its contribution is the finite-set theory
connecting \(\ResidualFaithfulness\), \(\RepairAtomicity\),
\(\GroupSoundness\), and \(\PsiDeletionMonotonicity\) to pointwise equality of
grouped and contract repair predicates, together with the exactness boundary
showing when \(\GroupSoundness\) is characterized by grouped correctness.  This
paper does not introduce priority, optimization, or normative ranking over repairs.
It is a contract-relative reportability theorem, not a priority claim over all
abstraction or refinement treatments of explanations.

\paragraph{High-level versus low-level explanations.}
The distinction between implementation levers and reportable contract atoms is
an abstraction and interface problem with proof obligations.  A low-level
label can be useful for implementation, while still being the wrong unit of
reporting.  This paper makes the abstraction map explicit through \(\beta\) and
\(\groupTouchAny\), then requires either atomicity or \(\GroupSoundness\), plus
\(\ResidualFaithfulness\), before a grouped report is treated as report-correct
at the declared contract interface.

\paragraph{SAT-based computational social choice.}
Computer-aided impossibility proofs and SAT-based rule search provide the
computational social-choice context
\citep{tanglin2009computer,geist2011automated,brandtgeist2016strategyproof}.
Those works motivate finite encodings, solver-backed evidence, and the need to
separate finite artifacts from broader theorem claims.  This paper is not a new
impossibility proof and does not supply finite-to-general transfer.  It starts
after a reference residual has been declared and asks when repairs to an
implementation residual may be reported against that reference.  The Arrow
discussion in this paper is therefore a scope boundary, not a second
instantiation of the present result; transfer limitations and theorem-specific transfer questions
remain separate obligations \citep{grandiendriss2013}.

\paragraph{Formal verification of social choice.}
Mechanized social-choice theorems in HOL provide an important proof-layer
precedent \citep{nipkow2009social}.  The present project uses Lean 4
\citep{moura2021lean4} and proof-carrying SAT infrastructure informed by
certified clausal proof checking \citep{cruzfilipe2017lrat,wetzler2014drat}.
Our Lean modules mechanize abstract finite-set reportability theorems.  They
do not formalize CNF generation, SAT solving, or the Candidate B artifact
enumeration.  That separation is deliberate: the paper combines a
kernel-checked theorem core with an artifact-backed instantiation, without
claiming an artifact-to-Lean bridge in this pass.

\paragraph{Relation to our prior work.}
This paper is part of a connected line of work.  An auditable finite atlas for
a small social-choice impossibility setting was established
in~\citep{hayashida2026atlas}.  A companion study~\citep{hayashida2026repair}
used Candidate B to isolate a raw-repair non-canonicity gap: a trusted witness
does not fix the level at which repairs should be reported.  A finite semantic
obstruction basis~\citep{hayashida2026obstruction} separated proof-layer
transfer from witness/audit-layer transfer.  The present paper adds the
repair/report layer: explicit reportability contracts, non-atomic
\(\GroupSoundness\), exactness under monotone contracts, and a contract-level
grouped report-correctness result on the same artifact-defined witness that
exposed the raw-level gap.
