\section{Discussion}
\label{sec:discussion}

\paragraph{Two simultaneous conclusions.}
Candidate B has two meanings at once.  At the raw implementation level it
remains a negative witness: the split realization exposes singleton
\(\RawRepair\) deletions for \(\mathtt{decisive\_voter0}\) and
\(\mathtt{decisive\_voter1}\), while the bundled realization reports the
coarser \(\mathtt{minlib}\) lever.  This paper does not make those raw families equal.
At the grouped artifact-defined contract level, the same witness is positive:
under the verified contract, \(\ResidualFaithfulness\), \(\GroupSoundness\),
and touch-any grouping, the grouped split report coincides with the bundled
contract repair family.  This is a statement about the level at which repairs
may be reported, not about which repair should be chosen.

\paragraph{Contract scope.}
An artifact-defined contract takes recorded bundled residuals as the reference
predicate.  A semantic contract would independently justify those residuals as
the intended social-choice problems; a Lean-level contract would tie that
meaning to formal definitions and theorems.  This paper proves reportability relative
to the chosen predicate.  It does not silently turn artifact evidence into a
semantic social-choice contract, and it does not turn the Candidate B audit into
a Lean-level formalization.  Those upgrades are separate truth/certificate
obligations.

\paragraph{Why reportability must be earned.}
Implementation labels are not automatically explanation categories.
Atomicity earns reportability syntactically; group soundness earns it for
non-atomic interfaces by requiring feasible partial-block deletions to remain
feasible after grouping; deletion monotonicity explains when that soundness
condition becomes necessary for grouped correctness.  The retained-set
convention keeps these obligations explicit: feasibility is always evaluated on
the residual that remains after deletion, not on the deletion label itself.
The finite examples in the Lean core show that these distinctions are
substantive, not merely terminological.  \(\ResidualFaithfulness\) and
\(\GroupSoundness\) are the explicit, auditable price of contract-relative
reporting correctness.  When those obligations are unavailable, this paper does
not prove the coarse report false; it shows that the report has not earned the
contract-relative guarantee established in this paper.

\paragraph{Interpretive boundary.}
This paper does not show that minimal liberalism should be relaxed.  It characterizes
when two distinct person-indexed implementation repairs may be reported under
the common contract atom \(\mathtt{minlib}\) without altering the
contract-level minimal-repair family.  In richer institutional
interpretations, person-indexed raw repairs may correspond to substantively
different interventions.  This paper does not decide whether those differences should
be exposed or suppressed; it characterizes only when a declared grouping is
report-correct.

\paragraph{Program boundary.}
The paper fits a larger program moving from auditable finite atlases toward
broader social-choice claims.  It contributes the repair/report component, not
a family-scale bridge theorem.  New theorem families require their own
reference residuals, evidence packages, and transfer arguments before the
present results can consume them.  In particular, Arrow remains a truth/certificate prerequisite
testbed: its residual lattice would need its own transfer legitimacy before any
repair/report comparison could be claimed.

\paragraph{Conclusion.}
The paper separates two questions that are often conflated.  One question is
whether an impossibility residual is validly certified.  Another is whether a
repair to an implementation residual may be reported as a repair to a declared
contract atom.  This paper does not choose or rank repairs.  It identifies the
auditable obligations required to compress distinct implementation repairs into
a common contract-level report without changing the declared contract repair
family.  Our prior study~\citep{hayashida2026repair} shows why reportability
cannot be assumed; this paper gives finite-set conditions under which it can be
earned.
