\section{Background And Running Lineage}

\subsection{Finite Social-Choice Artifacts}

M4 works with finite social-choice artifacts rather than unrestricted
social-choice theory. A finite artifact may record that a requirement set is
unsatisfiable, that a relaxed requirement set is satisfiable, that a particular
witness caused the conflict, or that a proposed deletion repairs it. Those are
useful statements, but they are not all the same kind of statement. An
impossibility result, a satisfiability result, a witness report, and a repair
presentation each depend on different pieces of evidence.

The background question for this paper is therefore not only whether a finite
artifact was checked. It is what the artifact is entitled to report. A repair
claim may require more than an UNSAT certificate; a grouped reporting claim may
require more than a list of raw repairs; a semantic claim may require more than
a successful finite enumeration. M4 treats these as trust-boundary questions.
It asks which reporting claims are licensed under a declared encoding and
which stronger claims must remain future correctness obligations.

\subsection{The Sen24 Setting}

The running case is Sen24: two voters and four alternatives. It is deliberately
small. The point of using such a small case is not that the finite instance
settles social choice in general, but that its relevant finite structure can
be audited completely. In this setting, the artifact can enumerate the finite
status table, distinguish SAT and UNSAT behavior, and inspect repair/reporting
structure without relying on sampling.

Sen24 is used here as a small complete audit case, not as a substitute for the
general Sen theorem. It is rich enough to contain nontrivial impossibility and
repair behavior, but controlled enough that the claim boundary can be stated
precisely. This makes it a useful case study for asking what a formal
social-choice artifact may report once its finite evidence, semantic
assumptions, and implementation assumptions are separated.

\subsection{The M1--M3 Lineage}

M1 supplies the finite-artifact discipline for the base Sen24 atlas. It
separates Proof, Audit, Witness, and Assumption obligations, so that a checked
artifact is not treated as a single undifferentiated source of authority. That
separation is inherited here as background discipline.

M1.5 shows that valid finite impossibility evidence does not determine a
canonical raw repair presentation. Even when an impossibility result is
accepted, there can be multiple legitimate ways to present repairs. This is
why M4 treats repair presentation as a reporting claim that must be audited
rather than assumed.

M2 contains the semantic bridge and the general Sen theorem. That result is
project background, not a new M4 claim. M4 does not re-prove M2, and it does
not use the finite Sen24 artifact as a replacement for the general theorem.

M3 gives reportability conditions under which grouped repair reports can be
justified relative to a declared contract. Its role here is conceptual: it
explains why grouped reports need their own contract conditions. M4 remains a
finite claim-boundary audit under a declared encoding, not a wholesale
reconstruction of the M3 theorem core.

\subsection{The Remaining M4 Question}

The remaining question is:

\begin{quote}
Given a declared finite encoding and a repair/reporting interface, what
exactly may the artifact report, and where must the report stop?
\end{quote}

M4 answers this question by separating four layers. First, Section~3 declares
the finite encoding boundary for the Sen24 artifact. Second, Section~4 gives
the finite 48-cell audit under that declared boundary. Third, Section~5 ties
the central right-condition target to a partial Lean-backed semantic target.
Fourth, Sections~6 and~8 state the future correctness obligations that are not
crossed here, including Python/CNF and semantic-to-CNF bridges.

This organization is meant to prevent a common over-reporting error. A finite
certificate can support a precise finite reporting claim without also proving
that the Python generator, every generated clause, and the Lean semantic
notions have all been connected by an end-to-end correctness theorem. M4 keeps
those layers visible.

\subsection{Background Boundary}

This paper uses the prior Sen-Lean4 program only to position the M4
claim-boundary audit. It does not claim a new general Sen theorem; that belongs
to M2. It does not prove semantic-to-CNF correctness, Python encoder
correctness, generated-clause correctness, or CNF artifact correctness. Its
claim is narrower: under the declared encoding, the finite Sen24 artifact is
audited for what repair and reporting statements it may make, while the
remaining implementation and semantic-correctness bridges are recorded as
future correctness obligations.
