\section{Declared Encoding And Scope}

\subsection*{Why Declare An Encoding?}

A finite audit needs a fixed interface. M4 therefore declares the finite
encoding under which its repair and reporting structure is audited. This
declaration is not a proof that the implementation is semantically correct.
It is a way to make the trust boundary visible: readers can separate claims
that are internal to the finite artifact interface from stronger claims about
Python code, generated clauses, or Lean-level social-choice semantics.

In this paper, ``under the declared encoding'' means that the claim is made
inside that artifact interface. It does not mean that the interface has already
been proved equivalent to the Lean definitions or to every generated CNF
artifact. That stronger correspondence is an encoding-correctness obligation
and remains future Level C work.

\subsection*{Active Scope}

The active scope is the Sen24 finite case: two voters and four alternatives.
Within that scope, M4 uses the declared selector-free semantic encoding
documented by the project. The encoding provides the paper-facing artifact
interface for repair and reporting. It uses bundled residual masks over the
active assumptions, fixed right-condition witnesses for the liberal-rights
component, and obstruction shapes computed from witness-pair overlap.

The declared interface also distinguishes SAT and UNSAT cells. Section~4 will
state the resulting 48-cell finite audit, but this section only fixes the
interface on which that audit depends. The point is to keep the later
certificate statement conditional on the declared encoding rather than to
silently promote it into a semantic equivalence theorem.

\subsection*{Coordinates Of The Audit}

The finite audit uses three main coordinates. A bundled mask records the
retained or active assumption interface for a residual case. An obstruction
shape records the structural form of the witness configuration. A cell is a
finite combination of a bundled mask and an obstruction shape under the
declared encoding.

If described as a phase diagram, the phrase means a table of these finite
cases and their audited statuses. It does not mean a general structural
theorem. In the same way, the mask-shape collapse pattern discussed by the
project should be read here as the observed and certified finite collapse
pattern under the declared encoding, not as a structural proof of why the
pattern must hold.

\subsection*{What The Declaration Licenses}

The declaration licenses finite-data statements inside the declared M4
interface. It supports status classification of enumerated cells,
repair/reporting claims conditional on that interface, paper-facing
certificate statements about the finite cases, and comparisons between mask
behavior and shape behavior within the declared Sen24 scope.

These statements are useful precisely because their scope is explicit. They
can be audited as finite artifact claims without pretending that every
semantic and implementation bridge has already been crossed.

\subsection*{What Remains Outside The Declaration}

This section does not establish Python encoder correctness,
\code{\_right\_clauses} correctness, SAT assignment semantics as Lean social
welfare functions, CNF artifact correctness, semantic-to-CNF correctness, full
selector-free equivalence to Lean \code{MINLIB}, or any family-scale lift.
Those items are outside what the declaration itself licenses. Sections~6
and~8 give the full claim-boundary and limitation lists.

Section~4 therefore uses this declared interface to present the finite audit.
It should be read as a certificate-style statement inside the declared M4
artifact interface, not as an independent expansion of the paper's claim
boundary.
