\section{Finite Audit}
\label{sec:finite-audit}

The declared encoding fixed above turns the M4 evidence object into a finite
audit. The audit is not a theorem about all
social choice settings, and it is not a proof that any Python or CNF artifact
faithfully implements the intended semantics. It is a complete finite-data
check of the declared Sen24 interface: bundled residual masks, fixed-witness
right atoms, and obstruction shapes.

The basic audit unit is a cell
\[
  \mathrm{Cell}(T,s),
\]
where \(T\) is a bundled residual mask and \(s\) is one of the obstruction
shapes \(O2\), \(O3\), or \(O4\). The distinction matters. The mask \(T\)
is the residual schema being audited; the shape \(s\) is an analysis coordinate
computed from the fixed witness package. Thus the audit does not redefine a
residual theory as a mask--shape pair. It stratifies each mask by the shape of
its internal fixed-witness instances and then checks the resulting finite
table.

Only minlib-active masks enter this phase diagram, because fixed-witness
right atoms are generated only after the bundled minlib schema is active.
There are 16 such bundled masks and three obstruction shapes, yielding
48 cells. The Certificate~2 checker covers all 48 cells under the declared
encoding. Its summary is shown in Table~\ref{tab:m4-finite-audit}.

\begin{table}[t]
\centering
\small
\begin{tabularx}{\linewidth}{@{}>{\raggedright\arraybackslash}p{0.20\linewidth}>{\raggedright\arraybackslash}p{0.34\linewidth}>{\raggedright\arraybackslash}X@{}}
\toprule
Audited item & Result & Interpretation \\
\midrule
Cell coverage
  & 16 minlib-active masks \(\times\) 3 shapes \(=48\) cells
  & The phase diagram is exhaustive for the declared mask--shape interface. \\
Cell status
  & 18 \texttt{ALL\_UNSAT}, 30 \texttt{ALL\_SAT}, no mixed or unknown cells
  & Each audited cell has a uniform status over its fixed-witness instances. \\
SAT cells
  & Active \texttt{RepairEmpty} for all 30 SAT cells
  & SAT cells are checked as satisfiable fixed-witness theories with no repair-object target. \\
UNSAT cells
  & 816 repair objects, 46 repair orbits, 46 cell report fibers
  & Each nonempty cell-indexed grouped-report fiber is exactly one complete repair orbit. \\
Shape-blind reports
  & 33 shape-blind fibers, support truncation checked
  & Shape-blind reporting ranges only over the UNSAT shape support of a mask/report pair. \\
Non-circularity
  & Passed
  & The residual class is not defined by repair behavior, orbit behavior, or shape support. \\
\bottomrule
\end{tabularx}
\caption{Certificate~2 finite audit under the declared M4 encoding.}
\label{tab:m4-finite-audit}
\end{table}

The SAT side is part of the certificate, not merely an absence of generated
rows. For every \texttt{ALL\_SAT} cell, the checker verifies that the
fixed-witness theories in the cell are satisfiable and that no repair object is
created for them. In this paper's terminology, those cells satisfy
\texttt{RepairEmpty}: there is no UNSAT repair target in the cell, and the
empty deletion is not counted as a repair.

The UNSAT side carries the repair-geometry claim. For each
\texttt{ALL\_UNSAT} cell, repair objects are indexed by the residual mask,
the fixed witness package, and the semantic repair. The group
\[
  S_2 \times S_4
\]
acts by voter swap and alternative relabeling. The audit checks that this
action is well-defined on repair objects, that the grouped-report map is
invariant under the action, and that the orbit-stabilizer equation holds for
each repair object. Most importantly for reporting, every nonempty
cell-indexed grouped-report fiber is exactly one complete repair orbit. Thus,
within an UNSAT cell, the grouped report identifies a full orbit of repairs
rather than a partial fragment or an accidental union of unrelated orbits.

The mask-only view leaves some bundled masks with both SAT and UNSAT witness
instances. The mask--shape audit explains this mixedness without making shape
part of the ambient theory identity. Once the witness instances are stratified
by \(O2\), \(O3\), and \(O4\), no cell is internally mixed: there are no
\texttt{MIXED\_WITHIN\_SHAPE} cells and no \texttt{UNKNOWN} cells. When a
report is later viewed without its shape coordinate, the certificate applies a
support-truncation law. Shape-blind fibers are evaluated only over the UNSAT
shape support of the corresponding mask/report pair; SAT shapes contribute no
repair objects. The checker records 33 such shape-blind fibers and verifies
that the orbit count in each blind fiber is exactly the size of its UNSAT shape
support.

These facts license the finite-data statement used by the rest of the paper:
under the declared selector-free Sen24 encoding, the M4 artifacts provide a
complete bundled-mask by obstruction-shape phase diagram, with SAT cells
classified as \texttt{RepairEmpty}, UNSAT cells satisfying orbit/fiber
exactness, shape-blind reports governed by support truncation, and no mixed or
unknown cells. They do not license stronger claims. In particular, this
section does not prove Python \texttt{\_right\_clauses} correctness, CNF
artifact correctness, semantic-to-CNF correctness, full equivalence to Lean
\texttt{MINLIB}, a structural Mask--Shape Collapse Law, or a family-scale
theorem of Sen.
