\section{Lean-Backed Semantic Target}

The finite audit in M4 is carried out under a declared finite encoding. That
encoding is the object audited by the certificate claims in this paper. Still,
one central concept should not float entirely at the artifact level: the
right-condition used in the finite audit should have a clear semantic target.
For this reason M4 includes a small Lean bridge. The bridge is a partial
semantic anchor, not an artifact-correctness result.

The Lean-backed target is implemented in
\code{SocialChoiceAtlas/Sen/RightAtomBridge.lean}. Its central definition is:

\[
\texttt{RightAtomSemantics}\ F\ i\ x\ y :=
x \ne y \land \texttt{Decisive}\ F\ i\ x\ y.
\]

In prose, \code{RightAtomSemantics} says that the two alternatives are
distinct and that a fixed voter \(i\) is decisive over the ordered pair
\((x,y)\). The semantic content is therefore expressed through the existing
Lean predicate \code{Decisive}, with endpoint distinctness included explicitly.
This gives the central right condition a Lean-level meaning while preserving
the declared-encoding boundary used by the finite audit.

The bridge also records orientation invariance. The M4 artifact-level right
condition is used with an unordered pair of alternatives, while Lean
\code{Decisive} is stated for an ordered presentation. The Lean theorems
\code{rightAtomSemantics_symm} and \code{rightAtomSemantics_iff_swap} record
that reversing the ordered presentation of the two alternatives does not
change the underlying semantic target. This relies on the corresponding
symmetry of \code{Decisive}. It is a semantic statement about the target, not a
proof that any particular Python clause block is correct.

The file also proves the sufficient direction from two fixed right conditions
to minimal liberalism. The theorem \code{twoRightAtoms_imply_MINLIB} states
that if two distinct voters satisfy \code{RightAtomSemantics} for their
respective pairs, then Lean \code{MINLIB} follows. This is useful because the
M4 finite audit works with fixed right-condition witnesses. The Lean bridge
shows that such a fixed two-right package is sufficient for the existing Lean
notion of \code{MINLIB}.

\begin{center}
\small
\begin{tabularx}{\linewidth}{@{}>{\raggedright\arraybackslash}p{0.30\linewidth}>{\raggedright\arraybackslash}p{0.25\linewidth}>{\raggedright\arraybackslash}X@{}}
\toprule
Lean-backed item & Status & What it licenses \\
\midrule
\code{RightAtomSemantics} &
Defined semantic target &
Gives the central right condition a Lean-level meaning \\
Orientation invariance &
Lean-backed &
Ordered presentation of the two alternatives does not alter the target \\
\code{twoRightAtoms_imply_MINLIB} &
Sufficient direction &
Connects two fixed right conditions with distinct voters to Lean
\code{MINLIB} \\
Python/CNF correspondence &
Not proved &
Future Level C obligation \\
\bottomrule
\end{tabularx}
\end{center}

This bridge matters for claim-boundary discipline. It prevents the finite
audit from being presented as a purely syntactic artifact report, because the
central right condition is tied to a Lean semantic predicate. At the same time,
it preserves the boundary between semantic anchoring and artifact correctness.
The finite audit remains a finite audit under the declared encoding; the Lean
bridge identifies a semantic target and proves limited semantic facts about
that target.

This bridge is intentionally limited. It does not prove Python/CNF artifact
correctness, semantic-to-CNF correctness, full selector-free equivalence to
Lean \code{MINLIB}, that the finite certificate is semantically correct as a
whole, or any family-scale lift. Those remain future Level C obligations or
outside M4 scope.
