\section{Reproducibility And Artifact Binding}
\label{sec:reproducibility}

This appendix binds the M4 preprint draft to repository-local sources and
documented evidence. It does not introduce a new solver run, a new generated
artifact, or a new proof of encoding correctness.

\subsection{Repository And Release Binding}

The repository is \code{SHayashida/Sen-Lean4}. The v0.1 release-candidate
source should be cited by the release tag or repository commit that contains
this appendix and the M4 release checklist.

The manuscript line that became this release candidate was originally prepared
after commit:

\begin{quote}
\texttt{8e060ff}, the draft-start commit for the claim-boundary manuscript
line.
\end{quote}

That commit is historical provenance only. A public release or archive should
bind the paper to the final release or tag commit, not to the draft-start
commit above.

\subsection{Main Source Files}

The M4 manuscript sources are:

\begin{itemize}[leftmargin=*]
\item \code{papers/m4/main.tex};
\item \code{papers/m4/CLAIM_BOUNDARY.md};
\item \code{papers/m4/README.md};
\item \code{papers/m4/sections/*.tex};
\item \code{papers/m4/refs.bib}.
\end{itemize}

\code{papers/m4/CLAIM_BOUNDARY.md} is the claim-boundary source of truth for
the preprint. The manuscript prose should not broaden those claims.
The related-work and reproducibility additions in this draft are bibliographic
and documentary. They do not change the finite-audit evidence, the declared
encoding, or the Lean source files.

\subsection{Lean Bridge Source}

The Lean-backed semantic target discussed in Section~5 is implemented in:

\begin{quote}
\code{SocialChoiceAtlas/Sen/RightAtomBridge.lean}.
\end{quote}

The confirmed Lean-backed items are:

\begin{itemize}[leftmargin=*]
\item \code{RightAtomSemantics};
\item \code{rightAtomSemantics_symm};
\item \code{rightAtomSemantics_iff_swap};
\item \code{twoRightAtoms_imply_MINLIB}.
\end{itemize}

These items provide a Level B semantic target for the central right condition.
They do not prove Python/CNF artifact correctness or semantic-to-CNF
correctness.

\subsection{Finite-Audit Source Documents}

The finite-audit claims in Section~\ref{sec:finite-audit} are grounded in the
following repository documents:

\begin{itemize}[leftmargin=*]
\item \code{docs/m4_semantic_encoding_boundary.md};
\item \code{docs/m4_scope_decision_mask_shape_phase_diagram.md};
\item \code{docs/m4_mask_shape_collapse_law_audit_result.md};
\item \code{docs/m4_certificate2_phase_diagram_checker_result.md};
\item \code{docs/m4_finite_data_closure_note.md}.
\end{itemize}

Together these documents record the declared encoding boundary, the
mask--shape analysis unit, the 48-cell phase-diagram audit, SAT-cell
\code{RepairEmpty}, UNSAT-cell orbit/fiber exactness, shape-blind support
truncation, and the explicit non-claims around Lean theorem status,
semantic-to-CNF correctness, and family-scale generalization.
The appendix cites these documents as manuscript evidence bindings. It does
not claim that their temporary output paths are release artifacts, and it does
not require those temporary directories to be regenerated for this draft.

\subsection{Build Command}

The lightweight manuscript build used for this draft is run from
\code{papers/m4/}:

\begin{quote}
\small
\begin{verbatim}
lualatex -interaction=nonstopmode -halt-on-error \
  -output-directory=/tmp/sen_m4_latex_build main.tex
\end{verbatim}
\end{quote}

With bibliography resolution, the draft uses:

\begin{quote}
\small
\begin{verbatim}
lualatex -interaction=nonstopmode -halt-on-error \
  -output-directory=/tmp/sen_m4_latex_build main.tex
\end{verbatim}
\end{quote}
\begin{quote}
\small
\begin{verbatim}
cd /tmp/sen_m4_latex_build
\end{verbatim}
\end{quote}
\begin{quote}
\small
\begin{verbatim}
BIBINPUTS=/path/to/Sen-Lean4/papers/m4: bibtex main
\end{verbatim}
\end{quote}
\begin{quote}
\small
\begin{verbatim}
cd /path/to/Sen-Lean4/papers/m4
\end{verbatim}
\end{quote}
\begin{quote}
\small
\begin{verbatim}
lualatex -interaction=nonstopmode -halt-on-error \
  -output-directory=/tmp/sen_m4_latex_build main.tex
\end{verbatim}
\end{quote}
\begin{quote}
\small
\begin{verbatim}
lualatex -interaction=nonstopmode -halt-on-error \
  -output-directory=/tmp/sen_m4_latex_build main.tex
\end{verbatim}
\end{quote}

No M4-specific \code{make} target is currently defined.
The generated PDF, auxiliary files, bibliography files, and logs produced by
these commands are build outputs. They should not be committed unless a later
paper-release policy explicitly says otherwise.

\subsection{What Is Not Reproduced Here}

No new solver run is part of this preprint draft. No CNF or LRAT artifacts are
regenerated here. No Level C semantic-to-CNF correctness proof is provided.
The appendix binds the manuscript to documented evidence and source files; it
does not claim to regenerate the finite-audit pipeline or to verify generated
artifacts end to end. In particular, this appendix should not be read as a
claim that Python clause generation, SAT assignment semantics, or CNF artifact
correctness has been proved. Those remain future correctness obligations under
the paper's Level C terminology.
