\begin{abstract}
Trustworthy finite impossibility evidence requires separating proof, audit, and witness concerns; but even after that separation is achieved, a further question arises: does the witness determine a canonical repair presentation?
A companion manuscript (M1) addresses the first layer---proof, audit, and witness separation---for the Sen24 base case.
This paper addresses the second layer.
Working strictly in the Sen24 base case \((n,m)=(2,4)\) and within the local-rationality setting induced by \code{no\_cycle3} and \code{no\_cycle4}, we compare two lever-structured encodings of the same impossibility boundary: a bundled encoding with a single liberalism lever \code{minlib}, and a split encoding exposing person-specific levers \code{decisive\_voter0} and \code{decisive\_voter1}.
The two encodings are clause-multiset equivalent---they produce identical CNF clause multisets up to variable renaming---and both are UNSAT.
We define raw repair explanation directly at the lever level and introduce a natural lever correspondence that transports bundled repairs to the split lever family.
Under this transport, the bundled singleton repair \code{minlib} maps to the pair \{\code{decisive\_voter0},\;\code{decisive\_voter1}\}; but on the split side, each person-specific lever is individually a minimal repair, so the transported pair is not inclusion-minimal there.
The transported and actual repair families therefore do not coincide.
We state this as an existence theorem: raw repair explanation is not invariant under clause-equivalent encodings, even when compared through the natural lever correspondence.
The implication is normative: finite witness legitimization can certify that a boundary is real, but it does not automatically determine a canonical repair presentation.
Audit-oriented repair reporting therefore requires an explicit abstraction contract specifying how repairs are to be compared or grouped across encodings.
\end{abstract}
