\section{Introduction}

Finite impossibility results in social choice theory have increasingly been supported by SAT-based verification, which allows finite witness certificates to stand in for axiomatic proofs over infinite preference domains \citep{tanglin2009computer,geist2011automated}.
A natural follow-up question arises once such a witness has been made trustworthy: once a solver has certified that a given combination of axioms is unsatisfiable, does that certificate also determine which axioms to relax and how to present the resulting repairs?
The answer matters because audit-oriented use is explanation-oriented.
A solver output is rarely consumed as a bare UNSAT certificate; it is turned into a recommendation about which design commitment should be relaxed.
If that recommendation depends on representational choices rather than on the underlying impossibility alone, then a valid witness does not by itself deliver a canonical repair presentation.

One might hope that this gap disappears under a strong enough comparison notion.
If two encodings of the same impossibility boundary are not merely logically related but \emph{clause-multiset equivalent}---identical CNF clause multisets up to variable renaming, written $\equiv_{\mathsf{CM}}$---then surely the raw repair explanation should also agree?
This paper shows that it does not.
The comparison is carried out in the strongest representational-equivalence setting we can construct in the Sen24 base case: exact $\equiv_{\mathsf{CM}}$, not merely logical equivalence or satisfiability-status agreement.
Even so, the raw lever-level minimal repair families differ under the natural lever correspondence between the two encodings.

The connection to diagnosis is direct.
In the MUS/MCS and explanation-oriented diagnosis literature \citep{dekleer1986atms}, the granularity of fault representation is known to affect the structure of explanations.
The present paper isolates the same phenomenon in the finite social choice witness setting, under a stronger comparison guarantee than is typical: exact clause-multiset equivalence rules out the cheap explanation that one encoding is simply logically stronger or weaker than the other.
The non-canonicality is therefore not a consequence of logical-strength drift; it is a structural feature of lever-level minimality under differing granularity.

Concretely, the paper studies the Sen24 base case \((n,m)=(2,4)\) \citep{sen1970}: a two-voter, four-alternative instance of Sen's Liberal Paradox.
Two encodings are compared: one uses a single bundled liberalism lever \code{minlib}, the other resolves it into person-specific levers \code{decisive\_voter0} and \code{decisive\_voter1}.
These encodings satisfy $\equiv_{\mathsf{CM}}$, yet the bundled singleton repair $\{\mathsf{minlib}\}$ transports to a two-element set that is not inclusion-minimal on the split side, where each person-specific lever is individually a minimal repair.

The paper's contribution is a theorem showing that $\equiv_{\mathsf{CM}}$ does not guarantee canonical raw repair explanation, together with a normative corollary: finite witness legitimization alone does not settle repair presentation.
Audit-oriented repair reporting requires an explicit abstraction contract specifying how repairs are to be compared or grouped across encodings.
This identifies a missing layer between witness validity and repair presentation; to our knowledge, this layer has not previously been isolated under an exact clause-multiset comparison guarantee in the finite social-choice witness literature.

The paper stays deliberately narrow.
All claims are about the Sen24 base case \((n,m)=(2,4)\), not about arbitrary Sen or Arrow families.
The rationality levers \code{no\_cycle3} and \code{no\_cycle4} are treated only as local-rationality approximations, not as full \code{SocialAcyclic}.
The main result is an existence theorem grounded in one audited base-case comparison, not a general repair theory.

The rest of the paper is organized as follows.
Section~\ref{sec:scope} fixes scope, notation, and the local-rationality setting.
Section~\ref{sec:definitions} gives the theorem-facing definitions, including clause-multiset equivalence ($\equiv_{\mathsf{CM}}$), natural lever correspondence, and repair transport.
The paper's contributions are summarized in Section~\ref{sec:contributions}.
Section~\ref{sec:theorem} presents the base-case witness and proves the non-canonicality theorem.
Section~\ref{sec:related} positions the paper relative to diagnosis, MUS/MCS explanation, SAT-based computational social choice, and related work on finite witness methodology.
Section~\ref{sec:conclusion} concludes with limitations, open questions, and the abstraction-contract thesis.
