\section{Main Theorem and Witness}
\label{sec:theorem}

The grounding artifact bundle for this section is
\code{results/20260401/candidate\_b\_minlib\_granularity/}.
Within that bundle, the main witness is the paired comparison between the bundled instance
\code{asymm+un+minlib+no\_cycle4}
and the split instance
\code{asymm+un+decisive\_voter0+decisive\_voter1+no\_cycle4}.
All claims below remain within the current local-rationality setting and the Sen24 base case.

\begin{theorem}[Non-invariance of raw repair explanation under natural lever correspondence]
\label{thm:non-invariance}
There exist lever-structured encodings $(\Lambda_b,\mathcal{S}_b,\varphi_b)$ and $(\Lambda_s,\mathcal{S}_s,\varphi_s)$, together with active lever sets $S_b \in \mathcal{S}_b$ and $S_s \in \mathcal{S}_s$, and a natural lever correspondence $\pi : \Lambda_b \to 2^{\Lambda_s}$ (Definition~\ref{def:transport}), such that:
\begin{enumerate}[label=(\arabic*),leftmargin=1.8em]
\item $\varphi_b(S_b) \equiv_{\mathsf{CM}} \varphi_s(S_s)$;
\item both $\varphi_b(S_b)$ and $\varphi_s(S_s)$ are $\mathsf{UNSAT}$;
\item the transported bundled repair family does not coincide with the split-side repair family:
\[
  \pi_*\!\bigl(\mathsf{Rep}^{\mathrm{raw}}_{\Lambda_b}(\varphi_b(S_b))\bigr)
  \neq
  \mathsf{Rep}^{\mathrm{raw}}_{\Lambda_s}(\varphi_s(S_s)).
\]
\end{enumerate}
\end{theorem}

\begin{proof}
We use the explicit Candidate~B witness pair recorded in
\code{results/20260401/candidate\_b\_minlib\_granularity/summary.md}
and \code{comparison.json}.

\medskip
\noindent\textbf{Step 1 (Witness identification).}
Define $\Lambda_b$ to be the bundled five-lever family
$\{\mathsf{asymm},\, \mathsf{un},\, \mathsf{minlib},\, \mathsf{no\_cycle3},\, \mathsf{no\_cycle4}\}$,
and let $S_b = \{\mathsf{asymm},\, \mathsf{un},\, \mathsf{minlib},\, \mathsf{no\_cycle4}\}$.
Define $\Lambda_s$ to be the split six-lever family
$\{\mathsf{asymm},\, \mathsf{un},\, \mathsf{decisive\_voter0},\, \mathsf{decisive\_voter1},\, \mathsf{no\_cycle3},\, \mathsf{no\_cycle4}\}$,
and let $S_s = \{\mathsf{asymm},\, \mathsf{un},\, \mathsf{decisive\_voter0},\, \mathsf{decisive\_voter1},\, \mathsf{no\_cycle4}\}$.
Let $\varphi_b$ and $\varphi_s$ denote the corresponding repository encodings.
Define the natural lever correspondence $\pi : \Lambda_b \to 2^{\Lambda_s}$ by
\[
  \pi(\mathsf{minlib}) = \{\mathsf{decisive\_voter0},\, \mathsf{decisive\_voter1}\},
\]
with all other levers mapping to their singletons (see Remark~\ref{rem:pi-witness}).

\medskip
\noindent\textbf{Step 2 (Clause-multiset equivalence and UNSAT status).}
The mapped comparison artifact reports that the bundled and split witness instances are clause-multiset equivalent under the designated variable-renaming map (Definition~\ref{def:clause-multiset-equiv}).
Both instances have $36{,}290$ clauses over $6{,}936$ variables.
The bundled instance assigns $13{,}826$ clauses to the lever category \code{minlib};
the split instance assigns $6{,}913$ clauses each to \code{decisive\_voter0} and \code{decisive\_voter1},
with $6{,}913 + 6{,}913 = 13{,}826$.
Both instances are $\mathsf{UNSAT}$.
Hence conditions~(1) and~(2) are satisfied.

\medskip
\noindent\textbf{Step 3 (Bundled raw repair family).}
Write $a,u,m,c_4$ for the levers \code{asymm}, \code{un}, \code{minlib}, and \code{no\_cycle4}.
The artifact summary reports the following raw lever-level minimal repair family on the bundled side:
\[
  \mathsf{Rep}^{\mathrm{raw}}_{\Lambda_b}(\varphi_b(S_b))
  = \bigl\{\{a\},\;\{u\},\;\{m\},\;\{c_4\}\bigr\}.
\]
All four minimal repairs are singletons: each individual lever in $S_b$ can be removed to restore satisfiability.

\medskip
\noindent\textbf{Step 4 (Transport through $\pi$).}
We compute the transported repair family.
The natural correspondence $\pi$ maps each singleton lever in $\Lambda_b$ to its split-side image:
\begin{align*}
  \pi(\{a\})   &= \{a\},  &
  \pi(\{u\})   &= \{u\},  \\
  \pi(\{m\})   &= \{d_0,\, d_1\},  &
  \pi(\{c_4\}) &= \{c_4\},
\end{align*}
where $d_0 = \mathsf{decisive\_voter0}$ and $d_1 = \mathsf{decisive\_voter1}$.
Therefore the transported bundled repair family is
\[
  \pi_*\!\bigl(\mathsf{Rep}^{\mathrm{raw}}_{\Lambda_b}(\varphi_b(S_b))\bigr)
  = \bigl\{\{a\},\;\{u\},\;\{d_0,d_1\},\;\{c_4\}\bigr\}.
\]
In particular, the bundled singleton repair $\{m\}$ becomes the two-element set $\{d_0,d_1\}$ under transport.

\medskip
\noindent\textbf{Step 5 (Split raw repair family).}
The artifact summary reports the following raw lever-level minimal repair family on the split side:
\[
  \mathsf{Rep}^{\mathrm{raw}}_{\Lambda_s}(\varphi_s(S_s))
  = \bigl\{\{a\},\;\{u\},\;\{d_0\},\;\{d_1\},\;\{c_4\}\bigr\}.
\]
All five minimal repairs are singletons: in particular, removing \code{decisive\_voter0} alone restores satisfiability, and removing \code{decisive\_voter1} alone also restores satisfiability.

\medskip
\noindent\textbf{Step 6 (Non-invariance).}
The transported bundled family and the split-side repair family are:
\begin{align*}
  \pi_*\!\bigl(\mathsf{Rep}^{\mathrm{raw}}_{\Lambda_b}(\varphi_b(S_b))\bigr)
  &= \bigl\{\{a\},\;\{u\},\;\{d_0,d_1\},\;\{c_4\}\bigr\}, \\[4pt]
  \mathsf{Rep}^{\mathrm{raw}}_{\Lambda_s}(\varphi_s(S_s))
  &= \bigl\{\{a\},\;\{u\},\;\{d_0\},\;\{d_1\},\;\{c_4\}\bigr\}.
\end{align*}
These two families differ.
The two-element set $\{d_0,d_1\}$ belongs to the transported family but \emph{not} to the split-side family, because $\{d_0\} \subsetneq \{d_0,d_1\}$ is already a minimal repair on the split side, so $\{d_0,d_1\}$ fails to be inclusion-minimal there.
Conversely, the singletons $\{d_0\}$ and $\{d_1\}$ belong to the split-side family but not to the transported family.
Therefore condition~(3) is satisfied.
\end{proof}

\begin{remark}[Why clause-equivalence is essential]
\label{rem:clause-essential}
Without clause-multiset equivalence, the difference between the bundled and split repair families could be attributed to a difference in logical strength between the two encodings.
In the present witness, $\varphi_b(S_b) \equiv_{\mathsf{CM}} \varphi_s(S_s)$: the two instances have identical clause structure up to variable renaming.
The non-invariance is therefore not a consequence of one encoding being stronger or weaker than the other.
It arises because the finer lever granularity of the split encoding makes person-specific singleton repairs visible, even though the underlying propositional content is clause-for-clause the same.
This is why the result is about \emph{minimality structure under lever granularity}, not about logical-strength drift.
\end{remark}

\begin{remark}[Witness interpretation]
\label{rem:interpretation}
The theorem is intentionally narrow.
It says only that such a witness exists in the Sen24 base case and within the current local-rationality setting.
It does not say that every clause-equivalent encoding pair must yield different raw repairs, nor does it characterize the full space of grouped repair invariance.
The broader mapped comparison artifact also reports clause-multiset equality and status preservation across all $32$ mapped bundled-to-split base-case packages.
That wider result strengthens confidence in the comparison methodology, but the proof above uses only the explicit witness pair.
\end{remark}

\begin{corollary}[Abstraction-contract corollary]
\label{cor:abstraction-contract}
Finite witness legitimization does not automatically determine a canonical repair presentation.
Even in clause-equivalent settings, audit-oriented repair presentation requires an explicit choice about how repair explanations are to be compared or grouped across encodings.
\end{corollary}

\paragraph{Discussion.}
The corollary is about presentation discipline, not about weakening the underlying impossibility witness.
The theorem shows that a proof-carrying or audit-carrying finite boundary can be stable while its raw repair explanation still changes with lever granularity.
Any grouped repair presentation that merges \code{decisive\_voter0} and \code{decisive\_voter1} into a single liberalism-level report is therefore an additional modeling choice, not a fact forced by the finite witness alone.
