\section{Limitations, Open Questions \& Conclusion}
\label{sec:conclusion}

\paragraph{Base-case limitation.}
The theorem is an existence result in the Sen24 base case only.
It does not claim that raw repair explanation is non-canonical for every encoding comparison, every theorem family, or every finite impossibility witness.
What is established is that the phenomenon already occurs in a tightly controlled setting where the comparison notion is as strong as we can make it: exact clause-multiset equivalence up to variable renaming.

\paragraph{Local-rationality limitation.}
All arguments in this paper remain inside the local-rationality setting induced by \code{no\_cycle3} and \code{no\_cycle4}.
Those levers are local forbidden-pattern approximations, not full \code{SocialAcyclic}.
Accordingly, the paper makes no full-acyclicity claim and no full Sen-family or Arrow-family generality claim.

\paragraph{What remains open.}
The main open problem is the repair-canonicalization layer itself.
This paper distinguishes raw repair explanation from grouped repair explanation, but it does not characterize when grouped repair explanations are canonical.
Future work may identify sufficient conditions on abstraction contracts under which grouped repair explanation becomes invariant.
That is an open question, not a theorem claimed here.

\paragraph{Repair geometry.}
The next conceptual step is to study the geometry induced by abstraction contracts:
which contracts preserve diagnosability, which collapse substantively different repairs, and which align with the social-choice semantics that an audit report wants to foreground.
That direction should build on the present distinction rather than erase it.

\paragraph{Conclusion.}
Clause-multiset equivalence ($\equiv_{\mathsf{CM}}$) is a strong comparison notion: two encodings that satisfy it are identical at the propositional level up to variable renaming.
Yet even $\equiv_{\mathsf{CM}}$ is not enough to force canonical raw repair explanation.
The base-case witness studied here shows that clause-equivalent bundled and split encodings can agree on the existence of an impossibility boundary while disagreeing on the raw lever-level minimal repair family.

The significance of the present result is not merely that bundled and split encodings yield different repair families.
Even under $\equiv_{\mathsf{CM}}$, a bundled repair presentation can mask finer person-specific minimal repairs that become visible only at a more granular leverization.
A trustworthy finite impossibility witness therefore does not, by itself, determine the granularity at which repairs should be reported.

In audit-oriented institutional design---including eventual AI-assisted settings where a solver output is consumed as an actionable recommendation---leaving that granularity choice implicit creates a concrete risk: a reviewer or downstream system may overlook finer minimal repairs and instead recommend a coarser, over-aggregated repair as if it were the natural one.
An abstraction contract is therefore not optional gloss but part of the reporting specification itself.
