\section{Reproducibility Note}
\label{sec:repro}

This manuscript is grounded in existing repository artifacts rather than new experiments.
The main evidence sources used in the text are:

\begin{itemize}[leftmargin=1.5em]
\item \code{docs/three_row_test_completed.md},
\item \code{docs/candidate_b_minlib_granularity.md},
\item \code{docs/candidate_a_collapse_note.md},
\item \code{docs/no_cycle_interpretation_note.md},
\item \code{results/20260401/candidate_b_minlib_granularity/summary.md},
\item \code{results/20260401/candidate_b_minlib_granularity/comparison.json},
\item \code{results/20260401/repair_liftability/liftability_step3.md}.
\end{itemize}

The relevant experiment bundle was recorded on branch
\code{codex/candidate-b-minlib-granularity}
with reference commit hash
\code{aa2e2c433920efb7b7104aadf69b77be9efe552b},
as noted in \code{docs/three_row_test_completed.md}.
The source code cited in this paper is available at
\url{https://github.com/SHayashida/Sen-Lean4/tree/codex/candidate-b-minlib-granularity}.

The manuscript workspace itself lives under \code{papers/m1_5/}.
The build command is:

\begin{quote}
\code{make -C papers/m1\_5 pdf}
\end{quote}

No new solver runs are part of this paper draft.
The role of this appendix is to point from the manuscript to the already existing repository artifacts that support the theorem statement and its scope restrictions.

\subsection{Manifest Evidence for Clause-Multiset Equivalence}
\label{sec:manifest-evidence}

The clause-multiset equivalence claim in Step~2 of the proof of Theorem~\ref{thm:non-invariance} is grounded in the solver manifest files for the two witness instances.

\paragraph{Bundled witness manifest}
(\code{results/20260401/candidate\_b\_minlib\_granularity/bundled/case\_11101/summary.json}):
\begin{center}
\begin{tabular}{ll}
\toprule
Field & Value \\
\midrule
\code{nclauses} & $36{,}290$ \\
\code{nvars}    & $6{,}936$ \\
\code{category\_counts.asymm}      & $6{,}912$ \\
\code{category\_counts.un}         & $1{,}728$ \\
\code{category\_counts.minlib}     & $13{,}826$ \\
\code{category\_counts.no\_cycle3} & $0$ \\
\code{category\_counts.no\_cycle4} & $13{,}824$ \\
\code{status} & \textsf{UNSAT} \\
\bottomrule
\end{tabular}
\end{center}

\paragraph{Split witness manifest}
(\code{results/20260401/candidate\_b\_minlib\_granularity/split/case\_111101/summary.json}):
\begin{center}
\begin{tabular}{ll}
\toprule
Field & Value \\
\midrule
\code{nclauses} & $36{,}290$ \\
\code{nvars}    & $6{,}936$ \\
\code{category\_counts.asymm}              & $6{,}912$ \\
\code{category\_counts.un}                 & $1{,}728$ \\
\code{category\_counts.decisive\_voter0}   & $6{,}913$ \\
\code{category\_counts.decisive\_voter1}   & $6{,}913$ \\
\code{category\_counts.no\_cycle3}         & $0$ \\
\code{category\_counts.no\_cycle4}         & $13{,}824$ \\
\code{status} & \textsf{UNSAT} \\
\bottomrule
\end{tabular}
\end{center}

\paragraph{Key observations.}
Both instances have identical total clause counts ($36{,}290$) and variable counts ($6{,}936$).
The bundled lever \code{minlib} contributes $13{,}826$ clauses;
on the split side, \code{decisive\_voter0} contributes $6{,}913$ clauses and \code{decisive\_voter1} contributes $6{,}913$ clauses, with $6{,}913 + 6{,}913 = 13{,}826$.
The clause counts for all other lever categories (\code{asymm}, \code{un}, \code{no\_cycle4}) are identical between the two instances.
This structure is consistent with a variable-renaming map $\rho$ that maps \code{minlib}-category variables to \code{decisive\_voter0}/\code{decisive\_voter1}-category variables while fixing all other variables.
The full clause-level bijection under $\rho$ is certified by the mapped comparison artifact in \code{comparison.json}, which reports \code{clause\_multiset\_equal: true} for this witness pair.

\subsection{Schematic Description of the Variable-Renaming Map}
\label{sec:renaming-map}

The variable-renaming map $\rho$ used to certify clause-multiset equivalence (Definition~\ref{def:clause-multiset-equiv}) has the following schematic structure:
\begin{itemize}[leftmargin=1.5em]
\item Variables belonging to the shared lever categories \code{asymm}, \code{un}, \code{no\_cycle3}, and \code{no\_cycle4} are \emph{fixed} by $\rho$: they have the same variable indices in both the bundled and split encodings.
\item Variables belonging to the bundled lever category \code{minlib} ($13{,}826$ clauses) are mapped by $\rho$ to the union of the split lever categories \code{decisive\_voter0} ($6{,}913$ clauses) and \code{decisive\_voter1} ($6{,}913$ clauses). The split encoding resolves each bundled \code{minlib} clause into exactly one clause under \code{decisive\_voter0} or \code{decisive\_voter1}, preserving the clause structure.
\item All clause counts outside \code{minlib}/\code{decisive\_voter}$i$ are identical between the two encodings, confirming that $\rho$ acts as the identity on the shared categories.
\end{itemize}
The full clause-by-clause bijection is certified by \code{comparison.json} across all $32$ mapped base-case packages.
For the specific witness pair used in Theorem~\ref{thm:non-invariance}, the comparison reports \code{clause\_multiset\_equal: true}.

\subsection{Artifact Grounding for the Raw Repair Families}
\label{sec:repair-artifact}

The raw minimal repair families stated in Steps~3 and~5 of the proof of Theorem~\ref{thm:non-invariance} are extracted from the artifact summary at
\code{results/20260401/candidate\_b\_minlib\_granularity/summary.md}
and the structured data in \code{comparison.json}.

\paragraph{Bundled side}
(witness: \code{asymm+un+minlib+no\_cycle4}, case \code{case\_11101}).
The artifact field \code{bundled\_min\_repairs} reports:
\begin{quote}
\code{["no\_cycle4", "minlib", "un", "asymm"]}
\end{quote}
Each entry is a single lever whose removal from the active set $S_b$ restores satisfiability,
and no proper subset of any such singleton is a repair (vacuously, since singletons have no proper nonempty subsets).
Therefore:
\[
  \mathsf{Rep}^{\mathrm{raw}}_{\Lambda_b}(\varphi_b(S_b))
  = \bigl\{\{\mathsf{asymm}\},\;\{\mathsf{un}\},\;\{\mathsf{minlib}\},\;\{\mathsf{no\_cycle4}\}\bigr\}.
\]

\paragraph{Split side}
(witness: \code{asymm+un+decisive\_voter0+decisive\_voter1+no\_cycle4}, case \code{case\_111101}).
The artifact field \code{split\_min\_repairs} reports:
\begin{quote}
\code{["no\_cycle4", "decisive\_voter1", "decisive\_voter0", "un", "asymm"]}
\end{quote}
Again, each entry is a single lever whose removal restores satisfiability.
Therefore:
\[
  \mathsf{Rep}^{\mathrm{raw}}_{\Lambda_s}(\varphi_s(S_s))
  = \bigl\{\{\mathsf{asymm}\},\;\{\mathsf{un}\},\;\{\mathsf{decisive\_voter0}\},\;\{\mathsf{decisive\_voter1}\},\;\{\mathsf{no\_cycle4}\}\bigr\}.
\]

\paragraph{Observation.}
Both repair families consist entirely of singletons.
On the bundled side there are four; on the split side there are five.
The critical difference is that the bundled singleton $\{\mathsf{minlib}\}$ transports to the two-element set $\{\mathsf{decisive\_voter0},\, \mathsf{decisive\_voter1}\}$, which is \emph{not} inclusion-minimal on the split side because each person-specific singleton is already a repair.
This is the artifact-level basis for Step~6 of the proof.
