\begin{abstract}
When an impossibility witness transfers to a larger finite case, its repair
explanation need not transfer with the same representational guarantees.
We study this issue in the Sen possibility-atlas pipeline, building on a base
case in which a bundled minimal-liberalism lever and a person-specific split
have the same clause multiset up to variable renaming, yet expose different raw
minimal repairs.  The question is whether that non-canonicity persists beyond
the two-voter, four-alternative instance.

The evidence is two-sided.  Along the alternative dimension, an isolated
two-voter encoding at $(n,m)=(2,5)$ preserves clause-multiset equivalence under
the identity renaming and preserves the raw repair divergence.  The bundled
singleton repair \lever{minlib} transports to a two-lever set, whereas the split
representation exposes two person-specific singleton repairs.  Along the voter
dimension, a pair-selector split at $(3,4)$ preserves UNSAT status but not
clause-multiset equivalence.  Role-specific selector machinery adds 12
variables and 165,888 clauses relative to the bundled encoding, yielding the
classification \texttt{sat\_equiv\_only}.  We therefore record a boundary
rather than infer repair non-canonicity for this case; repair enumeration for
the voter-dimension encoding is deliberately not performed.

The result is scoped to the local-rationality family defined by
\texttt{no\_cycle3} and \texttt{no\_cycle4}.  It is neither a claim about full
social acyclicity nor a family-level CNF certificate.  Methodologically, the
study shows why transfer claims about impossibility status, clause structure,
and repair presentation should be separated and audited independently.
\end{abstract}
