\section{Background and Scope}\label{sec:background}

\subsection{The local Sen atlas instance}

The finite packages considered here use five named levers:
\[
  \{\mathtt{asymm},\mathtt{un},\mathtt{minlib},
    \mathtt{no\_cycle3},\mathtt{no\_cycle4}\}.
\]
The first three represent asymmetry, unanimity, and a bundled
minimal-liberalism condition.  The final two forbid directed social cycles of
length three and four in the finite encoding.  Removing a lever removes the
corresponding clause family.  A raw repair is an inclusion-minimal set of
levers whose removal changes the active package from UNSAT to SAT\@.

The conjunction of the two no-cycle levers is called the
\emph{local-rationality family}.  It coincides with the relevant short-cycle
control at the $(2,4)$ base case, but it must not be identified with full
social acyclicity at family scale.  In particular, at $m=5$ it does not exclude
length-five cycles.  Every result below is interpreted inside this fixed
local-rationality family.

\subsection{Three distinct transfer questions}

The phrase ``the witness transfers'' can hide three different claims.
\begin{description}[style=nextline,leftmargin=2.2em]
  \item[Status transfer.]
  Do the compared packages have the same satisfiability status?
  \item[Clause-structure transfer.]
  Are their clause multisets equal up to a verified bijection on variables?
  \item[Repair-presentation transfer.]
  After the levers are aligned by a transport map, do the inclusion-minimal
  repair families agree?
\end{description}
Status agreement is weaker than clause-structure agreement.  Repair comparison
is interpretable under either relation, but its claim strength differs.
If the clause multisets coincide, logical-strength differences cannot explain a
repair divergence.  If only status agrees, extra selector clauses or other
encoding choices remain possible explanations.

This paper reserves the semantic impossibility-lift question for M2.  The M2.1
evidence does not modify the M2 theorem statements or their paper claims.
Instead, it treats the transferred finite cases as the setting in which the
repair representation is examined.

\subsection{Bundled and split liberalism}

The bundled representation exposes one lever, \texttt{minlib}.  At the
two-voter base case, the split representation exposes two person-specific
levers:
\[
  \mathtt{decisive\_voter0}
  \quad\text{and}\quad
  \mathtt{decisive\_voter1}.
\]
The repair-transport map $\pi$ aligns the two lever universes:
\[
\begin{aligned}
  \pi(\mathtt{minlib})
    &= \{\mathtt{decisive\_voter0},
          \mathtt{decisive\_voter1}\},\\
  \pi(x) &= \{x\}
  \quad\text{for }x\in
  \{\mathtt{asymm},\mathtt{un},
    \mathtt{no\_cycle3},\mathtt{no\_cycle4}\}.
\end{aligned}
\]
The map is a correspondence for comparing repair presentations.  It is not, by
itself, a semantic equivalence claim between axiom formulas.

For $n>2$, fixing voters 0 and 1 would no longer express the intended
existential choice of two witnesses.  The Option C design therefore changes
the split image to two roles,
\texttt{selected\_decisive\_left} and
\texttt{selected\_decisive\_right}, backed by a witness-pair selector bank.
That design preserves the intended choice among voters, but it also creates the
structural risk studied in Section~\ref{sec:option-c}.

\subsection{Artifact and trust boundary}

All M2.1 implementations remain exploratory and isolated under
\code{scripts/exploration/candidate_b/}.  They write reports to temporary local
directories.  They do not modify the production schema, production generators,
Lean files, baseline CNF or LRAT certificates, or tracked result directories.
The Option D scripts construct and compare the two-voter packages and enumerate
their raw repair families.  The Option C scripts stop after the Step~0
status-and-structure comparison.

This separation is important for the trust claim.  The committed Sen24
certificate establishes an audited base-case CNF fact; it is not a
family-level CNF certificate.  Likewise, the exploratory family comparisons
are evidence for the stated finite cases, not new kernel-checked theorem
statements.  Certified SAT and proof-assistant infrastructure remain relevant
to the broader atlas \citep{moura2021lean4,cruzfilipe2017lrat}, but the present
paper does not enlarge their certified scope.
