\section{Voter-Dimension Boundary (Option C)}\label{sec:option-c}

\subsection{Why the representation changes}

At $(3,4)$, two liberalism witnesses must be represented among three voters.
A direct reuse of the fixed voter-0/voter-1 split would hard-code a particular
pair and would not model the intended witness choice.  Option C therefore uses
a shared pair-selector bank and two exposed roles:
\[
  \pi(\mathtt{minlib}) =
  \{\mathtt{selected\_decisive\_left},
    \mathtt{selected\_decisive\_right}\}.
\]
The split levers share the selected witness pair but use separate decisive
selector banks so that each role can be removed independently.

The role distinction matters for the middle voter.  Voter 1 is the right member
of pair $(0,1)$ and the left member of pair $(1,2)$.  A split representation
that exposes left and right decisiveness separately must therefore retain two
role-specific series for that voter.  The bundled parametric
\texttt{minlib} encoding does not contain a one-to-one counterpart for all of
this split role structure.

\subsection{Step~0 measurements}

The Option C checker generates the repository's bundled
\texttt{pair\_selectors\_v1} package and the exploratory split package, then
solves both and checks necessary invariants for a variable-renaming bijection.
Table~\ref{tab:option-c} gives the measured result.

\begin{table}[ht]
\centering
\caption{Option C Step~0 result at $(3,4)$.}\label{tab:option-c}
\begin{tabular}{lrr}
\toprule
Measurement & Bundled & Split \\
\midrule
SAT status & UNSAT & UNSAT \\
Variables & 165,927 & 165,939 \\
Clauses & 1,347,847 & 1,513,735 \\
\bottomrule
\end{tabular}
\end{table}

The split package adds 12 variables and 165,888 clauses.  The additional
clauses are binary implications connecting the role-specific decisive
selectors to their content.  The variable count, total clause count, and
clause-length histogram differ.

\subsection{Refuting clause-multiset equivalence}

A variable renaming preserves the number of used variables, the number of
clauses including multiplicity, and the multiset of clause lengths.  Since all
three invariants differ, no bijection $\rho$ can turn the bundled clause
multiset into the split clause multiset.  Thus:
\[
  F_B\not\CM F_S.
\]
At the same time, both packages receive UNSAT status.  The four-way Step~0 classifier
therefore assigns
\[
  \mathtt{sat\_equiv\_only}.
\]

This classification is stronger than an inconclusive run: generation succeeds,
both statuses are established, and a structural invariant refutes \CM.  It is
weaker than the Option D control because status agreement does not remove
encoding-strength explanations.

\subsection{Gate consequence}

No Option C repair enumeration is performed.  The Step~0 protocol explicitly
requires a separate decision before a weaker, status-only repair comparison
could begin.  Such a comparison would answer a different question: how repair
families differ across satisfiability-equivalent but clause-distinct encodings.
It could not inherit the M1.5 claim that clause structure has been controlled.

Accordingly, the Option C evidence supports only the following boundary
statement:
\begin{quote}
At $(3,4)$, voter-dimension expansion preserves UNSAT status in the compared
bundled and pair-selector split packages, but the role-specific selector
machinery prevents transfer of the M1.5 clause-multiset-equivalence shield.
\end{quote}
It does not support a claim that repair non-canonicity persists at $(3,4)$.

\subsection{Why the negative side is informative}

The \CM{} failure is not a regression in Option D and not a failure of the
M2.1 program.  It identifies the point at which the witness representation must
do more work.  Along the alternative axis, the two witness series remain fixed
and can share the original clause basis.  Along the voter axis, the encoding
must represent witness choice and role.  The resulting structural delta is
therefore evidence about the boundary of the base-case witness class.

This distinction also prevents a common overinterpretation.  UNSAT/UNSAT
agreement alone does not imply that a repair explanation can be transported
without qualification.  Status can be stable while the explanatory vocabulary
and clause grouping change substantially.
